---
title: "Analyze Kinematic Analysis Tool Output"
author: "Ashley Henry"
date: "6/17/2019"
output: pdf
---

```{r setup, include=FALSE}
### Gets flf package loaded into environment ###
# install.packages("backports")
# install.packages("rcmdcheck")
# install.packages("devtools")
# install.packages("rowr")
# install.packages("plotly")
# setwd("/Users/ashleyhenry/")
devtools::load_all('/Users/ashleyhenry/flf')
library(flf)
library(ggplot2)
library(plotly)
library(tidyverse)
library(readr)
library(rowr)
require(reshape2)
# library(plyr)
```


```{r load-data, echo=FALSE}
### Creates path with folder of folders, each with one rawData.csv file
### Loads in all of the rawData.csv files ###
masterPath <- "/Users/ashleyhenry/Desktop/RILPop_Whole/imagingRound1/CviLer_RILs_1-10_1"

res <- processMasterFolder(masterPath)

### Creates numeric vector for means of the parameters ###
### Makes range of y from 0.0 to 3.5 px/hr ###
### pos values range from 0-2000 px from QC, increasing by 1 px at a time ###
ku         <- vector('numeric')
range_of_y <- range(0, 3.5)
pos        <- seq(0, 2000, 1)
```

```{r save-res-structure}
# Saves res structure (technically a "large list") to the working directory
## Saves data in a binary file
save(res, file = "res_CviLer_IAACtrl.RData")
# Loads res into environment
load("/Users/ashleyhenry/Desktop/Research/Kinematics/RCodeForExperiments/res_CviLer_IAACtrl.RData")
```

```{r parameters-summary}
### Loops through rawData.csv files from "res", calculates
#     mean parameters (x0, vf, k, n) for all rawData files 
#     Different genotypes separated by output file
#     (ex. 1 = 1st genotype/condition given)
#     "write.csv" saves parameters for each genotype in separate csv file
for (c in 1:length(res)){
  out <- plot_flfDataStructure(res[[c]], pos)
  # write.csv(out, paste('/Users/ashleyhenry/Desktop/ParameterSummaryandRawData_', as.numeric(c), '.csv', sep=""), row.names=F)
}

# generate vel curve for Ctrl Cvi & Cvi IAA
parameters_b4pin2 = res[[1]]$summary_table
parameters_b4 = res[[2]]$summary_table
parameters_Col = res[[3]]$summary_table
parameters_pin2 = res[[4]]$summary_table

t.test(parameters_CtrlCvi$vf, parameters_IAACvi$vf, alternative = c("two.sided"), paired = FALSE)
t.test(log(parameters_CtrlCvi$k), log(parameters_IAACvi$k), alternative = c("two.sided"), paired = FALSE)
t.test(log(parameters_CtrlCvi$n), log(parameters_IAACvi$n), alternative = c("two.sided"), paired = FALSE)

t.test(parameters_CtrlLer$vf, parameters_IAALer$vf, alternative = c("two.sided"), paired = FALSE)
t.test(log(parameters_CtrlLer$k), log(parameters_IAALer$k), alternative = c("two.sided"), paired = FALSE)
t.test(log(parameters_CtrlLer$n), log(parameters_IAALer$n), alternative = c("two.sided"), paired = FALSE)

# Melt data and get boxplots on same grid for all parameters
# MANUALLY CHANGE FOR CONDITION/GENOTYPE YOU NEED TO INVESTIGATE
parameters = res[[4]]$summary_table # same as above, makes variable to save parameter summary table

# parameters = res[[2]]$summary_table # Ler (Cvi above ^ )
# parameters = res[[3]]$summary_table # RIL1
# parameters = res[[4]]$summary_table # RIL2
# parameters = res[[5]]$summary_table # RIL3
# parameters = res[[6]]$summary_table # RIL4

# Melts "parameters" data to have 3 columns: fileName (replicate), variable (parameter), and value
parametersMelted = melt(parameters, id.var = "fileName")

# Boxplots for all parameters for condition/genotype
ggplot(data = parametersMelted, aes(x = variable, y = value)) + 
  geom_boxplot(aes(fill = variable)) +
  ylab("") +
  xlab("Parameters") +
  ggtitle("Distribution of Parameters") +
  theme_bw() +
  facet_wrap( ~ variable, scales = "free")

# addition on 11.19.2019, plot rawData.csv (pos&vel), overplot w/ fitted vel line
ggplot(data = data.frame(res[[1]]$rawData[[1]]), aes(x = pos, y = vel)) +
  geom_point() +
  ggtitle(res[[1]]$rawData[[1]]$fileName) #+
  # ylim(0, 3) +
  # xlim(0, 2000)

ggplot(data = data.frame(res[[4]]$rawData[[18]]), aes(x = pos, y = vel)) +
  geom_point() +
  ggtitle(res[[4]]$rawData[[18]]$fileName) #+
  # ylim(0, 3) +
  # xlim(0, 2000)

# Density Plots for each Parameter:
vfDist = ggplot(parameters, aes(x = vf)) +
  geom_density() +
  ggtitle("Cvi vf Density Plot")

kDist = ggplot(parameters, aes(x = k)) +
  geom_density() +
  ggtitle("Cvi k Density Plot")

nDist = ggplot(parameters, aes(x = n)) +
  geom_density() +
  ggtitle("Cvi n Density Plot")
```

```{r whatTheHellHappenedThisDay}
# Average Parameters for Ctrl Cvi
avgX0CtrlCvi = mean(parameters_CtrlCvi$x0) # 708.1485
avgVFCtrlCvi = mean(parameters_CtrlCvi$vf) # 3.090851
avgKCtrlCvi = mean(parameters_CtrlCvi$k) # 0.006933604
avgNCtrlCvi = mean(parameters_CtrlCvi$n) # 1.109034

# Average Parameters for Ctrl Cvi PLUS SD
avgX0CtrlCviPlusSD = mean(parameters_CtrlCvi$x0) + sd(parameters_CtrlCvi$x0) 
avgVFCtrlCviPlusSD = mean(parameters_CtrlCvi$vf) + sd(parameters_CtrlCvi$vf) 
avgKCtrlCviPlusSD = mean(parameters_CtrlCvi$k) + sd(parameters_CtrlCvi$k) 
avgNCtrlCviPlusSD = mean(parameters_CtrlCvi$n) + sd(parameters_CtrlCvi$n) 

# Average Parameters for Ctrl Cvi MINUS SD
avgX0CtrlCviMinusSD = mean(parameters_CtrlCvi$x0) - sd(parameters_CtrlCvi$x0) 
avgVFCtrlCviMinusSD = mean(parameters_CtrlCvi$vf) - sd(parameters_CtrlCvi$vf) 
avgKCtrlCviMinusSD = mean(parameters_CtrlCvi$k) - sd(parameters_CtrlCvi$k) 
avgNCtrlCviMinusSD = mean(parameters_CtrlCvi$n) - sd(parameters_CtrlCvi$n) 

x = seq(0, 2000)

avgCtrlCviVelProfile = flf(x, avgX0CtrlCvi, avgVFCtrlCvi, avgKCtrlCvi, avgNCtrlCvi)
avgCtrlCviVelProfilePlusSD = flf(x, avgX0CtrlCviPlusSD, avgVFCtrlCviPlusSD, avgKCtrlCviPlusSD, avgNCtrlCviPlusSD)
avgCtrlCviVelProfileMinusSD = flf(x, avgX0CtrlCviMinusSD, avgVFCtrlCviMinusSD, avgKCtrlCviMinusSD, avgNCtrlCviMinusSD)

CtrlCviwithSD = cbind(x, avgCtrlCviVelProfile, avgCtrlCviVelProfilePlusSD, avgCtrlCviVelProfileMinusSD)

plot(x, avgCtrlCviVelProfile)


write.csv(CtrlCviwithSD, paste('/Users/ashleyhenry/Desktop/CtrlCviwithandwithoutSD.csv', sep=""), row.names=F)

#######################################
########## AGAIN FOR IAA CVI ##########
#######################################
# Average Parameters for IAA Cvi
avgX0IAACvi = mean(parameters_IAACvi$x0) # 708.1485
avgVFIAACvi = mean(parameters_IAACvi$vf) # 3.090851
avgKIAACvi = mean(parameters_IAACvi$k) # 0.006933604
avgNIAACvi = mean(parameters_IAACvi$n) # 1.109034

# Average Parameters for IAA Cvi PLUS SD
avgX0IAACviPlusSD = mean(parameters_IAACvi$x0) + sd(parameters_IAACvi$x0) 
avgVFIAACviPlusSD = mean(parameters_IAACvi$vf) + sd(parameters_IAACvi$vf) 
avgKIAACviPlusSD = mean(parameters_IAACvi$k) + sd(parameters_IAACvi$k) 
avgNIAACviPlusSD = mean(parameters_IAACvi$n) + sd(parameters_IAACvi$n) 

# Average Parameters for IAA Cvi MINUS SD
avgX0IAACviMinusSD = mean(parameters_IAACvi$x0) - sd(parameters_IAACvi$x0) 
avgVFIAACviMinusSD = mean(parameters_IAACvi$vf) - sd(parameters_IAACvi$vf) 
avgKIAACviMinusSD = mean(parameters_IAACvi$k) - sd(parameters_IAACvi$k) 
avgNIAACviMinusSD = mean(parameters_IAACvi$n) - sd(parameters_IAACvi$n) 

IAACviwithSD = cbind(x, avgCtrlCviVelProfile, avgCtrlCviVelProfilePlusSD, avgCtrlCviVelProfileMinusSD)

plot(x, avgCtrlCviVelProfile)


write.csv(CtrlCviwithSD, paste('/Users/ashleyhenry/Desktop/CtrlCviwithandwithoutSD.csv', sep=""), row.names=F)

########## AGAIN FOR STANDARD ERROR ##########
# standard error = sd/sqrt(n)
# Standard errors for Parameters  
stderrorParameterx0 = sd(parameters_IAACvi$x0)/sqrt(36)
stderrorParametervf = sd(parameters_IAACvi$vf)/sqrt(36)
stderrorParameterk = sd(parameters_IAACvi$k)/sqrt(36)
stderrorParametern = sd(parameters_IAACvi$n)/sqrt(36)

avgX0IAACvi = mean(parameters_IAACvi$x0)
avgVFIAACvi = mean(parameters_IAACvi$vf)
avgKIAACvi = mean(parameters_IAACvi$k)
avgNIAACvi = mean(parameters_IAACvi$n)

avgX0IAACviPlusSD = avgX0IAACvi + stderrorParameterx0
avgVFIAACviPlusSD = avgVFIAACvi + stderrorParametervf
avgKIAACviPlusSD = avgKIAACvi + stderrorParameterk
avgNIAACviPlusSD = avgNIAACvi + stderrorParametern

avgX0IAACviMinusSD = avgX0IAACvi - stderrorParameterx0
avgVFIAACviMinusSD = avgVFIAACvi - stderrorParametervf
avgKIAACviMinusSD = avgKIAACvi - stderrorParameterk
avgNIAACviMinusSD = avgNIAACvi - stderrorParametern

x = seq(0, 2000)

avgIAACviVelProfile = flf(x, avgX0IAACvi, avgVFIAACvi, avgKIAACvi, avgNIAACvi)
avgIAACviVelProfilePlusSD = flf(x, avgX0IAACviPlusSD, avgVFIAACviPlusSD, avgKIAACviPlusSD, avgNIAACviPlusSD)
avgIAACviVelProfileMinusSD = flf(x, avgX0IAACviMinusSD, avgVFIAACviMinusSD, avgKIAACviMinusSD, avgNIAACviMinusSD)

IAACviwithSD = cbind(x, avgIAACviVelProfile, avgIAACviVelProfilePlusSD, avgIAACviVelProfileMinusSD)

plot(x, avgCtrlCviVelProfile)

write.csv(IAACviwithSD, paste('/Users/ashleyhenry/Desktop/IAACviwithandwithoutSD.csv', sep=""), row.names=F)
```


```{r EvaluateVelandREGRFits}

# Loops through all genotypes/conditions evaluating the equation at a 
## value, Pos (fixed position values (0-2000, increments of 1)), to 
## calculate velocity and REGR values using the maximum likelihood 
## estimate parameters for each replicate
# WARNING: Fits ALL replicates, not the average. To fit the avg vel, 
## look to the next code chunk
# Please Note: The final product has the correct units (hallelujah!)

for (i in 1:length(res)) {
  resultVel <- evaluateVelFits(res[[i]], pos)
  matrixEnd = ncol(resultVel) - 1
  for (j in 2:matrixEnd) {
    resultVel[,j] <- as.numeric(resultVel[,j]) * 0.08202 } # conversion from px/frame to mm/hr for all velocity value columns
  resultVel[,1] = as.numeric(resultVel[,1]) / 1463 # conversion from px to mm for the one position value column
  write.csv(resultVel, paste('/Users/ashleyhenry/Desktop/PosEvaluatedVel', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultVel[,1], resultVel[,2])
  
  ######################################
  
  resultREGR <- evaluateREGRFits(res[[i]], pos, 120*100)
  matrixEnd = ncol(resultREGR) - 1
  
  # for (k in 2:matrixEnd) {
    # resultREGR[,j] <- as.numeric(resultREGR[,j]) * 120} # DOESN'T WORK: conversion from px/frame*frame to px/frame*hr (or %/hr) for all velocity value columns
  
  resultREGR[,1] = as.numeric(resultREGR[,1]) / 1463 # WORKS: conversion from px to mm for the one position value column
  write.csv(resultREGR, paste('/Users/ashleyhenry/Desktop/PosEvaluatedREGR', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultREGR[,1], resultREGR[,2])
}
```

```{r plot-above-curves}
Cvi = read_csv("/Users/ashleyhenry/Desktop/PosEvaluatedREGR1.csv")
Ler = read_csv("/Users/ashleyhenry/Desktop/PosEvaluatedREGR2.csv")

Cvi = Cvi %>%
  rename(
    "Pos" = V1,
    # "Cvi_1" = V2 # Make for loop to label the replicate!
  )

Ler = Ler %>%
  rename(
    "Pos" = V1,
    # "Ler_1" = V2 # Make for loop to label the replicate!
  )

# Add dataset by dataset to make full dataset of Cvi & Ler for 2018 & 2019
CviLer = merge(Cvi,
               Ler,
               by = "Pos")

# Make merged dataset into long format
CviLongFormat = melt(Cvi, id.var = "Pos")
LerLongFormat = melt(Ler, id.var = "Pos")

# Graph genotype replicate data separately to see variance in genotype (do this for as many genotypes as you have, eventually do for loop)
ggplot(CviLongFormat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Root Tip (mm)") +
  ylab("Velocity from Root Tip (mm/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi, Ler, and RILs 1 - 4") +
  theme_bw()

ggplot(LerLongFormat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Root Tip (mm)") +
  ylab("Velocity from Root Tip (mm/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi, Ler, and RILs 1 - 4") +
  theme_bw()

```

```{r fitVelFromAvgParameters}
# MANUALLY CHANGE FOR CONDITION/GENOTYPE YOU NEED TO INVESTIGATE

# Note for order of res structure: 
# 1 = auxinCvi; 2 = auxinLer; 3 = ctrlCvi; 4 = ctrlLer
parameters = res[[1]]$summary_table

# parameters = res[[2]]$summary_table
# parameters = res[[3]]$summary_table
# parameters = res[[4]]$summary_table
# parameters = res[[5]]$summary_table
# parameters = res[[6]]$summary_table

# Averages the parameters, then fit velocty values to that pos and avg parameters
## Table that gives avg and sd for each paramters in that condition/genotype
parameter_summary = parameters %>%
  summarize(avg_x0 = mean(parameters$x0),
            sd_x0 = sd(parameters$x0),
            avg_vf = mean(parameters$vf),
            sd_vf = sd(parameters$vf),
            avg_k = mean(parameters$k),
            sd_k = sd(parameters$k),
            avg_n = mean(parameters$n),
            sd_n = sd(parameters$n))

# Matrix that has position values in 1st column and fitted velocity values in 2nd column
avgVelCurve <- matrix(nrow = length(pos), ncol = 2)
avgVelCurve[,1] <- pos
avgVelCurve[,2] <- flf(pos, parameter_summary$avg_x0, parameter_summary$avg_vf, parameter_summary$avg_k, parameter_summary$avg_n)

write.csv(avgVelCurve, paste('/Users/ashleyhenry/Desktop/avgVelCurve_pin2.csv'), row.names = F)

```

```{r plotVelCurves}
abcb4pin2 = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_abcb4pin2.csv")
abcb4 = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_abcb4.csv")
Col = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_Col.csv")
pin2 = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_pin2.csv")

abcb4pin2 = abcb4pin2 %>%
  rename(
    "Pos" = V1,
    "abcb4pin2" = V2
  )

abcb4 = abcb4 %>%
  rename(
    "Pos" = V1,
    "abcb4" = V2
  )

Col = Col %>%
  rename(
    "Pos" = V1,
    "Col" = V2
  )

pin2 = pin2 %>%
  rename(
    "Pos" = V1,
    "pin2" = V2
  )

# Change units from px/frame -> mm/hr
abcb4pin2$Pos = abcb4pin2$Pos/1463
abcb4pin2$abcb4pin2 = abcb4pin2$abcb4pin2*0.08202

abcb4$Pos = abcb4$Pos/1463
abcb4$abcb4 = abcb4$abcb4*0.08202

Col$Pos = Col$Pos/1463
Col$Col = Col$Col*0.08202

pin2$Pos = pin2$Pos/1463
pin2$pin2 = pin2$pin2*0.08202

# Save new file with correct units (mm & mm/hr) (!!!)
write.csv(abcb4pin2, paste('/Users/ashleyhenry/Desktop/avgVelCurve_abcb4pin2_CORRECTUNITS.csv'), row.names = F)
write.csv(abcb4, paste('/Users/ashleyhenry/Desktop/avgVelCurve_abcb4_CORRECTUNITS.csv'), row.names = F)
write.csv(Col, paste('/Users/ashleyhenry/Desktop/avgVelCurve_Col_CORRECTUNITS.csv'), row.names = F)
write.csv(pin2, paste('/Users/ashleyhenry/Desktop/avgVelCurve_pin2_CORRECTUNITS.csv'), row.names = F)

# Add dataset by dataset to make full dataset of Cvi & Ler for 2018 & 2019
abcb4pin2Abcb4 = merge(abcb4pin2,
               abcb4,
               by = "Pos")

abcb4pin2Abcb4Col = merge(Col,
               abcb4pin2Abcb4,
               by = "Pos")

abcb4pin2Abcb4Colpin2 =  merge(pin2,
               abcb4pin2Abcb4Col,
               by = "Pos") 
  
# Make merged dataset into long format
# CviLerRIL1234LongFormat = melt(CviLerRIL1234, id.var = "Pos")
abcb4pin2Abcb4Colpin2LongFormat = melt(abcb4pin2Abcb4Colpin2, id.var = "Pos")

# Graph 2018, 2019 CviLer_longformat data
ggplot(abcb4pin2Abcb4Colpin2LongFormat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Velocity from Root Tip (mm/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi, Ler, and RILs 1 - 4") +
  theme_bw()
```

```{r fitREGRFromAvgParameter}
  
# MANUALLY CHANGE FOR CONDITION/GENOTYPE YOU NEED TO INVESTIGATE
# Note: 
# 1 = auxinCvi; 2 = auxinLer; 3 = ctrlCvi; 4 = ctrlLer
parameters = res[[4]]$summary_table
# parameters = res[[2]]$summary_table
# parameters = res[[3]]$summary_table
# parameters = res[[4]]$summary_table
# parameters = res[[5]]$summary_table
# parameters = res[[6]]$summary_table

# Averages the parameters, then fit velocty values to that pos and avg parameters
## Table that gives avg and sd for each paramters in that condition/genotype
parameter_summary = parameters %>%
  summarize(avg_x0 = mean(parameters$x0),
            sd_x0 = sd(parameters$x0),
            avg_vf = mean(parameters$vf),
            sd_vf = sd(parameters$vf),
            avg_k = mean(parameters$k),
            sd_k = sd(parameters$k),
            avg_n = mean(parameters$n),
            sd_n = sd(parameters$n))

# Matrix that has position values in 1st column and fitted velocity values in 2nd column
avgREGRCurve <- matrix(nrow = length(pos), ncol = 2)
avgREGRCurve[,1] <- pos
avgREGRCurve[,2] <- REGR(pos, parameter_summary$avg_x0, parameter_summary$avg_vf, parameter_summary$avg_k, parameter_summary$avg_n, 12000)

write.csv(avgREGRCurve, paste('/Users/ashleyhenry/Desktop/avgREGRCurve_CtrlLer.csv'), row.names = F)

```

```{r plottingPracticeREGRCurves}
auxinCvi = read_csv("/Users/ashleyhenry/Desktop/avgREGRCurve_auxinCvi.csv")
auxinLer = read_csv("/Users/ashleyhenry/Desktop/avgREGRCurve_auxinLer.csv")
CtrlCvi = read_csv("/Users/ashleyhenry/Desktop/avgREGRCurve_CtrlCvi.csv")
CtrlLer = read_csv("/Users/ashleyhenry/Desktop/avgREGRCurve_CtrlLer.csv")

auxinCvi = auxinCvi %>%
  rename(
    "Pos" = V1,
    "auxinCvi" = V2
  )

auxinLer = auxinLer %>%
  rename(
    "Pos" = V1,
    "auxinLer" = V2
  )

CtrlCvi = CtrlCvi %>%
  rename(
    "Pos" = V1,
    "CtrlCvi" = V2
  )

CtrlLer = CtrlLer %>%
  rename(
    "Pos" = V1,
    "CtrlLer" = V2
  )

# Change units from px/frame -> mm/hr
auxinCvi$Pos = auxinCvi$Pos/1463
# abcb4pin2$abcb4pin2 = abcb4pin2$abcb4pin2*0.08202

auxinLer$Pos = auxinLer$Pos/1463
# abcb4$abcb4 = abcb4$abcb4*0.08202

CtrlCvi$Pos = CtrlCvi$Pos/1463
# Col$Col = Col$Col*0.08202

CtrlLer$Pos = CtrlLer$Pos/1463
# pin2$pin2 = pin2$pin2*0.08202

# Saves data now with correct units of mm and %/hr (!!!)
write.csv(abcb4pin2, paste('/Users/ashleyhenry/Desktop/avgREGRCurve_abcb4pin2_CORRECTUNITS.csv'), row.names = F)
write.csv(abcb4, paste('/Users/ashleyhenry/Desktop/avgREGRCurve_abcb4_CORRECTUNITS.csv'), row.names = F)
write.csv(Col, paste('/Users/ashleyhenry/Desktop/avgREGRCurve_Col_CORRECTUNITS.csv'), row.names = F)
write.csv(pin2, paste('/Users/ashleyhenry/Desktop/avgREGRCurve_pin2_CORRECTUNITS.csv'), row.names = F)

# Add dataset by dataset to make full dataset of Cvi & Ler for 2018 & 2019
auxin = merge(auxinLer,
               auxinCvi,
               by = "Pos")

auxinCtrlCvi = merge(auxin,
               CtrlCvi,
               by = "Pos")

auxinCtrl =  merge(auxinCtrlCvi,
               CtrlLer,
               by = "Pos") 
  
# Make merged dataset into long format
# CviLerRIL1234LongFormat = melt(CviLerRIL1234, id.var = "Pos")
auxinCtrl_LongFormat = melt(auxinCtrl, id.var = "Pos")

# Graph 2018, 2019 CviLer_longformat data
ggplot(auxinCtrl_LongFormat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Relative Elemental Growth Rate (%/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi, Ler, and RILs 1 - 4") +
  theme_bw()





############### Playing with data on 11.20.2019 ###############
######## Making plot of Cvi REGR Curve for proposal ###########

CtrlCvi = CtrlCvi %>%
  rename(
    "Pos" = V1,
    "CtrlCvi" = V2
  )

# Recalculate px -> mm & miscalculating REGR values to %
CtrlCvi$Pos = CtrlCvi$Pos/1463
CtrlCvi$CtrlCvi = CtrlCvi$CtrlCvi*0.08202

ggplot(CtrlCvi, aes(x = Pos, y = CtrlCvi)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Relative Elemental Growth Rate (%/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi, Ler, and RILs 1 - 4") +
  theme_bw()

```

# Sampling Random Subset of Data

This random sampling is to see how many replicates are needed for imaging. A random sampling of 5-10 replicates will be 
taken from the dataset of betweeen 18 and 36 replicates. If 5 replicates chosen at random (done several times) can produce 
the same fitted velocity curve as the original dataset, then only 5 replicates should be imaged in the future when imaging
the whole RIL population. Keep in mind these must be 5 ~good~ replicates.

```{r randomSubset}

###########################################
######### Graph of all Replicates #########
###########################################

## Load in data, rename columns, merge the Cvi & Ler datasets, turn merged dataset into long format, and then graph it!
LerAUXIN = read_csv("/Users/ashleyhenry/Desktop/avgFittedVel_AUXIN_Ler.csv")
LerCTRL = read_csv("/Users/ashleyhenry/Desktop/avgFittedVel_CTRL_Ler.csv")

LerAUXIN = LerAUXIN %>%
  rename(
    "Pos" = V1,
    "LerAUXIN" = V2
  )

LerCTRL = LerCTRL %>%
  rename(
    "Pos" = V1,
    "LerCTRL" = V2
  )

LerAUXINCTRL = merge(LerAUXIN,
                   LerCTRL,
                   by = "Pos")

LerAUXINCTRL_longformat = melt(LerAUXINCTRL, id.var = "Pos") # %>%
#   mutate(Pos_mm = Pos / 1463) %>%
#   mutate(value_mmhr = value * 0.08202)

# Graph 2019 Cvi and Ler data [ called "original" dataset i.e. before subsetting]
ggplot(LerAUXINCTRL_longformat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0,3.5) +
  xlab("Position from Root Tip (px)") +
  ylab("Velocity from Root Tip (px/frame)") +
  ggtitle("Control vs IAA Cvi and Ler") +
  theme_bw()

###########################################
####### Start subsetting replicates #######
###########################################

parameters = res[[1]]$summary_table # Makes variable to save parameter summary table

# How to select specific (either one or many) rows from res datatable
parameters[10,]
parameters[c(1,3,5,7,8),]

# Create your list of replicates you can choose from
## Ex: if had to remove replicate 24 from dataset, don't include 23 in your gIdx
## Note: Make specific name for each genotype/condition!!!
Cvi2019_gIdx = c(0:36)
Ler2019_gIdx = c(0:30)

# Create variable to save how many replicates to test at one time
## Start with 5-6, increase this if have to
idx = 5

# Get subset of summary_table data for previously randomly selected replicates
subsetReplicates = sort(sample(Cvi2019_gIdx, idx, replace = FALSE))
parametersSubset = parameters[c(subsetReplicates),]
View(parametersSubset)


```

