---
title: "AuxinTransportMutants_Analysis.Rmd"
author: "Ashley Henry"
date: "11/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all('/Users/ashleyhenry/flf')
library(flf)
library(ggplot2)
library(plotly)
library(tidyverse)
library(readr)
library(rowr)
require(reshape2)
library(dplyr)
library(naniar)
library(neldermead)
library(gridExtra)
library(performance)
library(numDeriv)
library(bigutilsr)
```

## Analysis of Auxin Transport Mutants
### Mutants with Col background: pin2, abcb4-1, abcb4-2, & abcb19-3

```{r load-data, echo=FALSE}
### Below is copied from AnalyzeKinematicAnalysisToolOutput.Rmd
### Creates path with folder of folders, each with one rawData.csv file
### Loads in all of the rawData.csv files ###
masterPath <- "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_RawData_KnownAlleles/Col_background"

# 11-23-2020
# loopValue = number of times I'm taking 90% of the data with the lowest residuals
# loopValue at 10 for whole RIL set
res <- processMasterFolder(masterPath, 15)

# Saves res structure (technically a "large list") to the working directory
## Saves data in a binary file
save(res, file = "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants.RData")

# Or if you already did this step:
load("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants.RData")
```

```{r plot-point-cloud-&-fitting, echo = FALSE}
# for loop to plot point cloud & fitted line on same graph
## Saves plot to Desktop/RILPop_plotsNEW/ for each replicate
## 12-07-2020
for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]])
    graphTitle = rawData$fileName[j]
    # Shorten fileName to the replicate name for simplicity
    # graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,8] #use for RILs
    graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,10] #use for IAA transport mutants
    print(graphTitle)
    fittedVel = flf(rawData$pos,
                    res[[i]]$summary_table$x0[j],
                    res[[i]]$summary_table$vf[j],
                    res[[i]]$summary_table$k[j],
                    res[[i]]$summary_table$n[j])
    
    print(ggplot(rawData, aes(x = rawData$pos)) +
      geom_point(aes(y = rawData$vel)) +
      geom_point(aes(y = fittedVel), color = "blue") +
      ggtitle(graphTitle) +
      xlab("Position from Root Tip (px)") +
      ylab("Velocity from Root Tip (px/frame)") +
      theme_bw())
    
    # fittedREGR = REGR(rawData$pos,
                    # res[[i]]$summary_table$x0[j],
                    # res[[i]]$summary_table$vf[j],
                    # res[[i]]$summary_table$k[j],
                    # res[[i]]$summary_table$n[j],
                    # 1)
    # print(fittedVel[1])
    # print(fittedREGR)
    
    # Saving each graph as .tiff takes up more space than .pdf, so using .pdf for full RILSet
    # graphName = paste('~/Desktop/RILPop_plotsNEW/', graphTitle, "_", i, '_pointCloudFittedVel.pdf', sep = "")
    # graphName = paste('~/Desktop/pux1Imaging/pux1_plots/', graphTitle, '_pointCloudFittedVel.pdf', sep = "")
    graphName = paste('~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/IAAMutant_Alleles_pointCloudFittedVel/', graphTitle, "_", i, '_pointCloudFittedVel.pdf', sep = "")
    # Saves plot to location written above ^
    ggsave(graphName)
  }
}

```

```{r Load-Res-Structures}

######################################################################
##### Note: This will combine all .RData files in the directory! #####
######################################################################

# Iteratively loads in all res structures from ~/rildata directory by:
## Loading RData file into new environment
## Then extracting res variable
loadRData <- function(fileName) {
  #loads an RData file, and returns it
  e1 = new.env()
  load(fileName, e1)
  get("res", e1)
}
# 
# Load in correct res structure
load("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants.RData")
load("~/Desktop/2021-12-15_res_CviLer.RData")


# Pulls filenames from directory
fils <- matrix(list.files("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/", pattern = "RData$", full.names = TRUE, recursive = TRUE))

# # Loading them into RES structure
RES <- lapply(fils, loadRData)
```

```{r Combine-Summary-Tables-of-Res-Structure}
############## function & for loop written on 30 January 2020 w/ Julian's help #############
####################### Copied from ParameterInvestigation.Rmd script ######################
# Function to separate res structure and rename pathname to filename for column "fileName" #
pathname_to_filename = function(genotype) {
  # Get genotype name from pathname
  genoName = basename(dirname(dirname(toString(genotype$fileName[[1]]))))
  # Create empty matrix of one column and as many rows as there are of res structure
  outnames = matrix(1, nrow(genotype))
  # outnames = matrix(1, as.numeric(nrow(genotype)))
  # Loops through each row of res
  ## Extracts pathname from each row in the dataframe
  ## Extracts filename from each pathname
  ## outnames = extracted filenames
  for (i in 1:nrow(genotype)) {
    namePlay_i  = toString(genotype$fileName[[i]])
    outnames[i] = basename(dirname(namePlay_i))
    print(outnames[i])
  }
  # Replaces pathname column with outnames column
  ## Now the column labeled "fileName" has filename instead of pathname
  genotype[["fileName"]] <- outnames
  # Return genotype summary table and genotype name
  gtype_gname = list(genotype, genoName)
  return(gtype_gname)
}

extractParameters = function(res) {
  # Create empty dataframe to fill with each RIL's parameters
  RILParameterSummaryTable = data.frame(matrix(
                                            ncol = 7, 
                                            nrow = 0, 
                                            dimnames = list(NULL, c("fileName", "x0", "vf", "k", "n", "meanAbsDiff", "matSlope"))))

  # for loop to call "pathname_to_filename" function for each genotype in res
  ## Fills dataframe with all replicates of all RILs' parameter summary tables
  for (i in 1:length(res)) {
    gtype = res[[i]]$summary_table
    gList = pathname_to_filename(gtype)
    summaryTable = gList[[1]]
    # eval(parse(text = paste0(sprintf("%s = gList[[1]]", gList[[2]])))) # removed this line 2021-11-23 b/c had issues & works w/out it
    RILParameterSummaryTable = rbind(RILParameterSummaryTable, summaryTable)
  }

  return(RILParameterSummaryTable)
}

# Uses function above to make summary table for parameters of all RILs
RILParams = lapply(RES, extractParameters)
RILParam_concatenated = bind_rows(RILParams)
# RILParam_concatenated = bind_rows(fileName) 

# Save progress
write.csv(RILParam_concatenated, file = "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants_SummaryParameters.csv")
```

```{r shorten-fileName-to-be-genotype}
# This code chunk creates a new column called "RILs" and fills that column with the shortened fileName
## This allows the RILs to be grouped together and averaged, because now they have the same name to be grouped
## Note: Revised on 2020-05-27 to add leading zeros before RIL number

# Start with file you just created (^), need to load() then get() to have in environment
# IAAMutants_SummaryParameters = load("~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_pux1Day3_SummaryParameters.csv")
# IAAMutants_SummaryParameters = get(IAAMutants_SummaryParameters)

IAAMutants_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants_SummaryParameters.csv")

# Makes a column of shortened RIL names by copying the fileName column
## Make copy of fileName column called RILs
# IAAMutants_SummaryParameters$RILs <- IAAMutants_SummaryParameters$fileName

# Used this for IAA mutants data analysis
## Note: I changed the Col names to be col manually in Excel to make this part easier
IAAMutants_SummaryParameters$mutants <- IAAMutants_SummaryParameters$fileName
IAAMutants_SummaryParameters$mutants <- str_split(IAAMutants_SummaryParameters$mutants, '_', simplify = TRUE)[,1]

# Save progress in csv file
write.csv(IAAMutants_SummaryParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants_SummaryParameters.csv")
```

```{r vel-fits-for-all-replicates}
# for loop to plot a fitted line for all replicates of one genotype on the same plot
## 05-02-2022
for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]])
    graphTitle = rawData$fileName[j]
    # Shorten fileName to the replicate name for simplicity
    # graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,8] #use for RILs
    graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,10] #use for IAA transport mutants
    print(graphTitle)
    fittedVel = flf(rawData$pos,
                    res[[i]]$summary_table$x0[j],
                    res[[i]]$summary_table$vf[j],
                    res[[i]]$summary_table$k[j],
                    res[[i]]$summary_table$n[j])
    
    print(ggplot(rawData, aes(x = rawData$pos)) +
      # geom_point(aes(y = rawData$vel)) +
      geom_point(aes(y = fittedVel), color = "blue") +
      ggtitle(graphTitle) +
      xlab("Position from Root Tip (px)") +
      ylab("Velocity from Root Tip (px/frame)") +
      theme_bw())
  }
}

```

# Begin outlier check
## Percent Maturation Zone
## Parameter Distributions
## 

```{r percent-mat-zone, echo = FALSE}
### Thought process:
# which() gives the index of the velocity/REGR points that are in k
# this index won't work on pos values in the rawData, b/c there are 8000+ indices & the disk locations repeat along the root
# need to grab the velocity values at that point, graph them to see where they are & pull THOSE vel values from the rawData
## As of 11:51 on 12-21-2020 I did the above task, now to add it to a for loop!

## Calculating percent of Maturation Zone for each root
# Finished code on 1-4-2021

percentofMatZone <- data.frame(filename = c(), percentofMatZone = c())

for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]]) 
    fileName = rawData$fileName[j]
    fileName = str_split(fileName, '/', simplify = TRUE)[,10]
    print(fileName)

    pos = c(1:3000)
    # Get velocity fits for example data
    fittedVel = flf(pos, 
                 res[[i]]$summary_table[2]$x0[j],	
                 res[[i]]$summary_table[3]$vf[j],	
                 res[[i]]$summary_table[4]$k[j],	
                 res[[i]]$summary_table[5]$n[j])

    # Get REGR fits for example data
    fittedREGR <- REGR(pos, 
                   res[[i]]$summary_table[2]$x0[j],	
                   res[[i]]$summary_table[3]$vf[j],	
                   res[[i]]$summary_table[4]$k[j],	
                   res[[i]]$summary_table[5]$n[j],
                   1)

    # REGRfit = data.frame(cbind(pos, fittedREGR))
    maxREGR = max(fittedREGR) # finds Vmax
    per = 0.2 # percentage of area under the curve we want
    maxVel = max(fittedVel) # finds vf

    velocityFit = data.frame(cbind(pos, fittedVel))
    # plot(velocityFit)

    # ggplot(REGRfit, aes(x = pos)) +
    #   geom_point(aes(y = fittedREGR))

    k = which((fittedREGR < maxREGR*per) & (fittedVel > maxVel*0.5)) # reports row number/column number of the cases that are "true"

    fittedVelofMatZone = fittedVel[k]
    # plot(pos[k], fittedVelofMatZone, ylim = c(0, max(fittedVelofMatZone)), xlim = c(0, 3000)) # just plots mat zone

    minVelofMatZone = min(fittedVelofMatZone) # find min value of vel that's in mat zone

    rawDatainMatZone = which(rawData$vel > minVelofMatZone)
    percentMatZone = (length(rawDatainMatZone)/length(res[[i]]$rawData[[j]]$vel))*100
    
    tmp <- data.frame(filename = fileName, percentofMatZone = percentMatZone)
    percentofMatZone <- rbind(percentofMatZone,tmp)
   
  }
  percentofMatZone
}

auxinMutants_PercentofMatZone = percentofMatZone
# write.csv(WholeRILSet_PercentofMatZone, "~/Desktop/01-04-2021_WholeRILSet_PercentofMatZone.csv")
write.csv(auxinMutants_PercentofMatZone, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_IAAMutants_PercentofMatZone.csv")


auxinMutants_PercentofMatZone = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_IAAMutants_PercentofMatZone.csv", header = TRUE) %>%
  select(-X)

ggplot(auxinMutants_PercentofMatZone, aes(percentofMatZone)) +
  geom_density() +
  ggtitle("Percentages of Position Values in Maturation Zone for IAA Transport Mutants") +
  theme_bw()

rootsWithZeroMatZone = auxinMutants_PercentofMatZone %>%
  filter(percentofMatZone < 0.0090)

rootswithLittleMatZone = auxinMutants_PercentofMatZone %>%
  filter(percentofMatZone < .9)

# Note: there are 56 of 1631 roots that have 0 position points within the defined maturation zone
# Also Note: Visually, would like the cut-off to be 0.9% of the maturation zone included. Anything >0.9%, I'm comfy keeping. 
## I'll look into those <0.9%

### Create dataset that removes the roots < 0.5% of the mat zones
IAAMutants_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants_SummaryParameters.csv") %>%
  select(-X, -X.1) %>%
  group_by(fileName)
# data = cbind(AllRILs_SummaryParameters, WholeRILSet_PercentofMatZone)
data = cbind(data.frame(IAAMutants_SummaryParameters), data.frame(auxinMutants_PercentofMatZone))
identical(data[,1], data[,9]) # Check if filename columns are identical
data = data.frame(data)
# Removes roots wth no maturation zone from dataset, leaving 1575 total roots
data = data %>%
  filter(percentofMatZone > 0.9)
# Write data to csv for later:
write.csv(data, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_13_IAAMutants_SummaryParameters-removedLittleMatZoneRoots.csv")


# ################################################################################
# ### Create dataset that removes 100 roots with few points in the mat zone
# AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv") %>%
#   select(-X) %>%
#   group_by(fileName)
# data = cbind(AllRILs_SummaryParameters, WholeRILSet_PercentofMatZone)
# identical(data[['fileName']],data[['fileName1']]) # Yes, these are identical columns
# data = data.frame(data)
# # Removes roots wth little (<0.5%) maturation zone from dataset, leaving 1497 total roots
# data = data %>%
#   # filter(percentofMatZone > 0.5)
#   filter(percentofMatZone > 0.0090)
# # Write data to csv for later:
# write.csv(data, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedLittleMatZoneRoots.csv")
# ################################################################################
```

```{r parameter-distributions-all-roots}
# Taking a look at the distribution of parameters with new dataset that doesn't contain outliers (roots without a mat zone)
# data = read.csv("~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedNoMatZoneRoots.csv")
data = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_13_IAAMutants_SummaryParameters-removedLittleMatZoneRoots.csv")
data = data %>%
  select(-X)
  # select(-X, -X.1, -X.2)

# Note: k and n still very skewed left, will need to do log transformation & try again! (code for that is below)
p1 = ggplot(data, aes(n)) +
  geom_density()
p2 = ggplot(data, aes(k)) +
  geom_density()
p3 = ggplot(data, aes(vf)) +
  geom_density()
p4 = ggplot(data, aes(x0)) +
  geom_density()

# Plot all density plots on one page
parameterDensityPlots_pin2 = grid.arrange(p1, p2, p3, p4, 
             ncol = 2, nrow = 2)
```

```{r PARAMETER-distributions-by-genotype}
# Outlier testing with density plots
IAAMutants_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_res_auxinMutants_SummaryParameters.csv")

# Make separate datasets for each mutant:
## abcb19
abcb19_3 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb19-3")
## abcb4-1
abcb4_1 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb4-1")
## abcb4-2
abcb4_2 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb4-2")
## abcb4-3
abcb4_3 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb4-3")
## pin2
pin2 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "pin2")
## Col-0 (WT)
Col_0 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "Col-0")

# Plot distribution plots of each parameter
dist_n = ggplot(Col_0, aes(n)) +
  geom_density() +
  xlab("Parameter n for Col-0") +
  theme_bw()

dist_k = ggplot(Col_0, aes(k)) +
  geom_density() +
  xlab("Parameter k for Col-0") +
  theme_bw()

dist_vf = ggplot(Col_0, aes(vf)) +
  geom_density() +
  xlab("Parameter vf for Col-0") +
  theme_bw()

dist_x0 = ggplot(Col_0, aes(x0)) +
  geom_density() +
  xlab("Parameter x0 for Col-0") +
  theme_bw()

# Plot all density plots on one page
parameterDensityPlots_pin2 = grid.arrange(dist_n, dist_k, dist_vf, dist_x0, 
             ncol = 2, nrow = 2)

```

```{r DESCRIPTOR-distributions-by-genotype}
# Outlier testing with density plots
IAAMutants_SummaryDescriptors = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_20_growthCurveDescriptors-wAlleles.csv")

# Make separate datasets for each mutant:
## abcb19
abcb19_3 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "abcb19-3")
## abcb4-1
abcb4_1 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "abcb4-1")
## abcb4-2
abcb4_2 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "abcb4-2")
## abcb4-3
abcb4_3 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "abcb4-3")
## pin2
pin2 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "pin2")
## Col-0 (WT)
Col_0 = IAAMutants_SummaryDescriptors %>%
  filter(IAAMutants_SummaryDescriptors$mutants == "Col-0")

# Plot distribution plots of each parameter
dist_maxREGR = ggplot(Col_0, aes(maxREGR)) +
  geom_density() +
  xlab("Max REGR for Col-0") +
  theme_bw()

dist_growthZoneWidth = ggplot(Col_0, aes(growthZoneWidth)) +
  geom_density() +
  xlab("Width of Growth Zone for Col-0") +
  theme_bw()

dist_vf = ggplot(Col_0, aes(vf)) +
  geom_density() +
  xlab("Overall Growth Rate for Col-0") +
  theme_bw()

dist_positionMaxREGR = ggplot(Col_0, aes(positionMaxREGR)) +
  geom_density() +
  xlab("Position of MaxREGR for Col-0") +
  theme_bw()

# Plot all density plots on one page
parameterDensityPlots_pin2 = grid.arrange(dist_maxREGR, dist_growthZoneWidth, dist_vf, dist_positionMaxREGR, 
             ncol = 2, nrow = 2)

##################################################################################


```
## Possible outliers as seen from density plots
* 

## Also, consider doing a log transformations on n and k (to keep with RIL processing)

```{r parameter-boxplots}
# Outlier Testing with Boxplots:
## Note: Manually change which genotype you're plotting!

# Do this again to check boxplots after outlier removal
IAAMutants_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2021_12_06_IAAMutants_SummaryParameters-removedLittleMatZoneRoots.csv") %>%
  select(-X, -X.1, -X1, -filename)

abcb19_3 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb19-3")
## abcb4-1
abcb4_1 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb4-1")
## abcb4-2
abcb4_2 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "abcb4-2")
## pin2
pin2 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "pin2")
## Col-0 (WT)
Col_0 = IAAMutants_SummaryParameters %>%
  filter(IAAMutants_SummaryParameters$mutants == "Col-0")

mutant = Col_0
boxplot_x0 = ggplot(mutant) +
  aes(x = "", y = x0) +
  geom_boxplot(fill = "blue") +
  xlab("Col_0") + 
  theme_bw()

boxplot_vf = ggplot(mutant) +
  aes(x = "", y = vf) +
  geom_boxplot(fill = "red") +
  xlab("Col_0") + 
  theme_bw()

boxplot_k = ggplot(mutant) +
  aes(x = "", y = k) +
  geom_boxplot(fill = "green") +
  xlab("Col_0") + 
  theme_bw()

boxplot_n = ggplot(mutant) +
  aes(x = "", y = n) +
  geom_boxplot(fill = "orange") +
  xlab("Col_0") + 
  theme_bw()

# Plot all four boxplots on one page, as done in last code chunk
parameterBoxplots = grid.arrange(boxplot_n, boxplot_k, boxplot_vf, boxplot_x0, 
             ncol = 2, nrow = 2)

# Now manually remove outliers that were dots on the boxplots!
```

```{r outlierTests-with-check_outliers()}
## Outlier Testing that Stuti suggested
mutant = Col_0
nrow(Col_0)
mutant = data.frame(mutant)
outliersList = check_outliers((mutant$n), method = c("zscore")) # Possible methods: "pareto", "cook", "zscore_robust", "iqr", "ci"
outliersList = check_outliers((mutant$x0), method = "zscore", threshold = 2)

# From check_outliers() R manual
outliers_list <- check_outliers(mutant$n) # Find outliers
as.data.frame(outliers_list) # Show the row index of the outliers
as.numeric(outliers_list) # The object is a binary vector...
filtered_mutant <- mutant[!outliers_list, ] # And can be used to filter outliers from a dataframe
nrow(filtered_mutant) # New size, 8 (1 outliers removed)
```

```{r barGraphs-of-parameters-by-genotype}
# Plot bar graphs of parameters
IAAMutants_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_13_IAAMutants_SummaryParameters-removedLittleMatZoneRoots.csv")
data = IAAMutants_SummaryParameters %>%
  # select(-X1, -fileName, -meanAbsDiff, -matSlope)
  select(-fileName, -filename, -X, -meanAbsDiff, -matSlope)

# Melt data to be long format for easy ggplot graphing
data_long = melt(data, ID.vars = "mutants")
# Separate out dataset by parameters
data_x0 = data_long %>%
  filter(variable == "x0")
data_vf = data_long %>%
  filter(variable == "vf")
data_k = data_long %>%
  filter(variable == "k")
data_n = data_long %>%
  filter(variable == "n")

# Now plot
ggplot(data_x0, aes(x = mutants)) +
  geom_bar(aes(y = value))
  
ggplot(data_long, aes(mutants, value)) +   
  geom_bar(aes(fill = variable), position = "dodge", stat = "identity")
```



# Average Parameters
```{r avg-parameters-by-mutant}
AllMutants_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_IAAMutants_SummaryParameters-removedLittleMatZoneRoots.csv") 

AllMutants_SummaryParameters = AllMutants_SummaryParameters %>%
  select(-X1, -filename, -fileName) %>%
  mutate(x0 = as.numeric(x0),
         vf = as.numeric(vf),
         k = as.numeric(k),
         n = as.numeric(n))

AllMutants_AveragedParameters = AllMutants_SummaryParameters %>%
  group_by(mutants) %>%
  select(-matSlope, -meanAbsDiff, -percentofMatZone) %>%
  summarise_each(funs(mean(., na.rm = TRUE))) # Added na.rm so that averages didn't calc in the NAs for the mean

AllMutants_StDevParameters = AllMutants_SummaryParameters %>%
  group_by(mutants) %>%
  select(-matSlope, -meanAbsDiff, -percentofMatZone) %>%
  summarise_each(funs(sd(., na.rm = TRUE))) 

# Save data as csv files
write.csv(AllMutants_AveragedParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_13_AllMutants_AveragedParameters.csv")
write.csv(AllMutants_StDevParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_13_AllMutants_StDevParameters.csv")
```

# Plot Velocity and REGR Profiles
```{r fittingVelCurves}
### Creates numeric vector for means of the parameters ###
### Makes range of y from 0.0 to 3.5 px/hr ###
### pos values range from 0-2000 px from QC, increasing by 1 px at a time ###
ku         <- vector('numeric')
range_of_y <- range(0, 3.5)
pos        <- seq(0, 2000, 1)
```

```{r plotting-velocity-profiles}
AllMutants_AvgParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_AllMutants_AveragedParameters.csv") %>%
  mutate(x0 = as.numeric(x0),
         vf = as.numeric(vf),
         k = as.numeric(k),
         n = as.numeric(n))

# In the averaged csv:
## 1 = abcb19-3
## 2 = abcb4-1
## 3 = abcb4-2
## 4 = abcb4-3
## 5 = Col-0
## 6 = pin2

abcb19_3 = flf(pos,
                      AllMutants_AvgParameters[1,]$x0,
                      AllMutants_AvgParameters[1,]$vf,
                      AllMutants_AvgParameters[1,]$k,
                      AllMutants_AvgParameters[1,]$n)
abcb4_1 = flf(pos,
                     AllMutants_AvgParameters[2,]$x0,
                     AllMutants_AvgParameters[2,]$vf,
                     AllMutants_AvgParameters[2,]$k,
                     AllMutants_AvgParameters[2,]$n)
abcb4_2 = flf(pos,
                   AllMutants_AvgParameters[3,]$x0,
                   AllMutants_AvgParameters[3,]$vf,
                   AllMutants_AvgParameters[3,]$k,
                   AllMutants_AvgParameters[3,]$n)
abcb4_3 = flf(pos,
                    AllMutants_AvgParameters[4,]$x0,
                    AllMutants_AvgParameters[4,]$vf,
                    AllMutants_AvgParameters[4,]$k,
                    AllMutants_AvgParameters[4,]$n)
Col_0 = flf(pos,
                    AllMutants_AvgParameters[5,]$x0,
                    AllMutants_AvgParameters[5,]$vf,
                    AllMutants_AvgParameters[5,]$k,
                    AllMutants_AvgParameters[5,]$n)
pin2 = flf(pos,
                    AllMutants_AvgParameters[6,]$x0,
                    AllMutants_AvgParameters[6,]$vf,
                    AllMutants_AvgParameters[6,]$k,
                    AllMutants_AvgParameters[6,]$n)

velCurves = cbind(pos, abcb19_3, abcb4_1, abcb4_2, abcb4_3, Col_0, pin2)
velCurves = data.frame(velCurves)
# write.csv(velCurves, "~/Desktop/2022-04-19_velCurves_IAAMutants.csv")

velCurves = velCurves %>%
  mutate(pos = pos/1500,
       abcb19_3 = abcb19_3*0.08,
       abcb4_1 = abcb4_1*0.08,
       abcb4_2 = abcb4_2*0.08,
       abcb4_3 = abcb4_3*0.08,
       pin2 = pin2*0.08,
       Col_0 = Col_0*0.08)

velCurves_long = melt(velCurves, id.vars = "pos")

write.csv(velCurves_long, "~/Desktop/2022-04-13_velCurves_long.csv")
velCurves_long = read.csv("~/Desktop/2022-04-13_velCurves_long.csv") %>%
  select(-X)

ggplot(velCurves_long, aes(x = pos, y = value)) +
  geom_point(aes(color = variable), size = 0.5) +
  scale_color_manual(values = c("blue", "orange", "violet", "red", "black", "green")) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Velocity from QC (mm/hr)") +
  ggtitle("Velocity Curves for Auxin Transport Mutants") +
  theme_bw()
```

```{r plotting-REGR-curves-IAA-mutants}
AllMutants_AvgParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022-04-13_AllMutants_AveragedParameters.csv") %>%
  mutate(x0 = as.numeric(x0),
         vf = as.numeric(vf),
         k = as.numeric(k),
         n = as.numeric(n))
pos        <- seq(0, 2000, 1)

# In the averaged csv:
## 1 = abcb19-3
## 2 = abcb4-1
## 3 = abcb4-2
## 4 = abcb4-3
## 5 = Col-0
## 6 = pin2

abcb19_3 = REGR(pos,
                      AllMutants_AvgParameters[1,]$x0,
                      AllMutants_AvgParameters[1,]$vf,
                      AllMutants_AvgParameters[1,]$k,
                      AllMutants_AvgParameters[1,]$n,
                      1)
abcb4_1 = REGR(pos,
                     AllMutants_AvgParameters[2,]$x0,
                     AllMutants_AvgParameters[2,]$vf,
                     AllMutants_AvgParameters[2,]$k,
                     AllMutants_AvgParameters[2,]$n,
                      1)
abcb4_2 = REGR(pos,
                   AllMutants_AvgParameters[3,]$x0,
                   AllMutants_AvgParameters[3,]$vf,
                   AllMutants_AvgParameters[3,]$k,
                   AllMutants_AvgParameters[3,]$n,
                      1)
abcb4_3 = REGR(pos,
                    AllMutants_AvgParameters[4,]$x0,
                    AllMutants_AvgParameters[4,]$vf,
                    AllMutants_AvgParameters[4,]$k,
                    AllMutants_AvgParameters[4,]$n,
                      1)
Col_0 = REGR(pos,
                    AllMutants_AvgParameters[5,]$x0,
                    AllMutants_AvgParameters[5,]$vf,
                    AllMutants_AvgParameters[5,]$k,
                    AllMutants_AvgParameters[5,]$n,
                      1)
pin2 = REGR(pos,
                    AllMutants_AvgParameters[6,]$x0,
                    AllMutants_AvgParameters[6,]$vf,
                    AllMutants_AvgParameters[6,]$k,
                    AllMutants_AvgParameters[6,]$n,
                      1)

REGRCurves = cbind(pos, abcb19_3, abcb4_1, abcb4_2, abcb4_3, Col_0, pin2)
REGRCurves = data.frame(REGRCurves)
# write.csv(REGRCurves, "~/Desktop/2022-04-19_REGRCurves_IAAMutants.csv")


REGRCurves = REGRCurves %>%
  mutate(pos = pos/1500,
       abcb19_3 = abcb19_3*10000,
       abcb4_1 = abcb4_1*10000,
       abcb4_2 = abcb4_2*10000,
       abcb4_3 = abcb4_3*10000,
       pin2 = pin2*10000,
       Col_0 = Col_0*10000)

REGRCurves_long = melt(REGRCurves, id.vars = "pos")
write.csv(REGRCurves_long, "~/Desktop/2022-04-13_REGRCurves_long.csv") # manually changed mutant's name to w/out alleles
REGRCurves_long = read.csv("~/Desktop/2022-04-13_REGRCurves_long.csv")

ggplot(REGRCurves_long, aes(x = pos, y = value)) +
  geom_point(aes(color = variable), size = 0.5) +
  scale_color_manual(values = c("blue", "orange", "violet", "red", "black", "green")) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Relative Elemental Growth Rate from QC (%/hr)") +
  ggtitle("REGR Curves for Auxin Transport Mutants") +
  theme_bw()
```

# T-tests Comparing Mutants & Col Wildtype

```{r t-tests-on-mutants-vs-Col}
AllMutants_GrowthTraits = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2022_04_20_growthCurveDescriptors-wAlleles.csv")

abcb4_1 = AllMutants_GrowthTraits %>%
  filter(mutants == "abcb4-1")
abcb4_2 = AllMutants_GrowthTraits %>%
  filter(mutants == "abcb4-2")
abcb19_3 = AllMutants_GrowthTraits %>%
  filter(mutants == "abcb19-3")
Col_0 = AllMutants_GrowthTraits %>%
  filter(mutants == "Col-0")

# Test for normality for each mutants' growth zone traits
# Plot distribution plots of each parameter
dist_maxREGR = ggplot(abcb19_3, aes(maxREGR)) +
  geom_density() +
  xlab("Trait maxREGR for abcb19_3") +
  theme_bw()

dist_posMaxREGR = ggplot(abcb19_3, aes(positionMaxREGR)) +
  geom_density() +
  xlab("Trait posMaxREGR for abcb19_3") +
  theme_bw()

dist_vf = ggplot(abcb19_3, aes(vf)) +
  geom_density() +
  xlab("Trait vf for abcb19_3") +
  theme_bw()

dist_growthZoneWidth = ggplot(abcb19_3, aes(growthZoneWidth)) +
  geom_density() +
  xlab("Trait growthZoneWidth for abcb19_3") +
  theme_bw()

# Plot all density plots on one page
parameterDensityPlots_pin2 = grid.arrange(dist_maxREGR, dist_posMaxREGR, dist_vf, dist_growthZoneWidth, 
             ncol = 2, nrow = 2)

t.test(abcb4_1$maxREGR, Col_0$maxREGR)
t.test(abcb4_2$maxREGR, Col_0$maxREGR)
t.test(abcb19_3$maxREGR, Col_0$maxREGR)
# all maxREGR are significantly different from Col-0

t.test(abcb4_1$vf, Col_0$vf)
t.test(abcb4_2$vf, Col_0$vf)
t.test(abcb19_3$vf, Col_0$vf)
# all vf are significantly different from Col-0

t.test(abcb4_1$growthZoneWidth, Col_0$growthZoneWidth)
t.test(abcb4_2$growthZoneWidth, Col_0$growthZoneWidth)
t.test(abcb19_3$growthZoneWidth, Col_0$growthZoneWidth)
# all growthZoneWidth are significantly different from Col-0

t.test(abcb4_1$positionMaxREGR, Col_0$positionMaxREGR)
t.test(abcb4_2$positionMaxREGR, Col_0$positionMaxREGR)
t.test(abcb19_3$positionMaxREGR, Col_0$positionMaxREGR)
# all positionMaxREGR are significantly different from Col-0

```







