---
title: "RIL Set Analysis Script"
author: "Ashley Henry"
date: "4/9/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
### Gets flf package loaded into environment ###
# install.packages("backports")
# install.packages("rcmdcheck")
# install.packages("devtools")
# install.packages("rowr")
# install.packages("plotly")
# install.packages("naniar")
# install.packages("performance")
# install.packages("numDeriv")
# install.packages("gridExtra")
# setwd("/Users/ashleyhenry/")
devtools::load_all('/Users/ashleyhenry/flf')
library(flf)
library(ggplot2)
library(plotly)
library(tidyverse)
library(readr)
library(rowr)
require(reshape2)
library(dplyr)
library(naniar)
library(neldermead)
library(gridExtra)
library(performance)
library(numDeriv)
```

# Script to Analyze RIL Set
__Note:__ 

## Script Completions:
* Loads in all clicking data into a res structure (complicated list of lists)
* Combines all res structures into one workable dataframe
* Relabels data as simplified RIL name (not path/filename)
* Balances out sample size (currently at less than/equal to 8 replicates)
* Calculates log(k) and log(n)
* Calculates average, median, st dev, & variance of the parameters for each RIL
* Goodness of fit for flf curve (R^2, show flf on point cloud for each RIL)
* Repeatable & efficient outlier testing (functions are in flf.R, run in this script)

```{r load-data, echo=FALSE}
### Below is copied from AnalyzeKinematicAnalysisToolOutput.Rmd
### Creates path with folder of folders, each with one rawData.csv file
### Loads in all of the rawData.csv files ###
# masterPath <- "~/Desktop/RILPop_tmp/"
masterPath <- "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_RawData"


# devtools::load_all('/Users/ashleyhenry/flf')
# library(flf)

# 11-23-2020
# loopValue = number of times I'm taking 90% of the data with the lowest residuals
# loopValue at 10 for whole RIL set
res <- processMasterFolder(masterPath, 15)

# Saves res structure (technically a "large list") to the working directory
## Saves data in a binary file
save(res, file = "~/rildata/rildata_realfullDataset/2020_12_07_res_RILPop_full.RData")
# save(res, file = "~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_res_pux1Day3.RData")
save(res, file = "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-27_res_auxinMutants-withCol.RData")


# Or if you already did this step:
# load("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-08-27_res_auxinMutants.RData")
load("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-10_res_auxinMutants-withCol.RData")
```

```{r drafting-code-block}
####################################################################################
# 11-24-2020, Cases with very low mle value correlated w/ little/no mat zone:
# give flf parameters & gives REGR growth rate (slope at last 10 points of the fit)
## IF that slope isn't ~0, then you likely didn't get enough maturation zone
# Create code to report out the -log(mean(slope[last 10 position points - mat zone])) to the res structure summary table
## Added this to flf.R on 12.1.2020!

# wholePosVel = read.csv("/Users/ashleyhenry/Desktop/RILPop_full/RIL1_1/RIL1--RIL1_001_1.5--/rawData.csv", header = FALSE)
# wholePosVel = wholePosVel %>%
#   rename(
#     pos = V1,
#     vel = V2
#   )
# # plot(wholePosVel$pos, wholePosVel$vel)
# 
# resValue = 1 # only use if have a small res sample!
# # 1 - make flf fit line
# fittedVel = flf(wholePosVel$pos, 
#                 res[[resValue]]$summary_table[2]$x0,	
#                 res[[resValue]]$summary_table[3]$vf,	
#                 res[[resValue]]$summary_table[4]$k,	
#                 res[[resValue]]$summary_table[5]$n)
# fittedposVel = cbind(wholePosVel$pos, fittedVel) # makes matrix of pos & fitted vel values for g truth parameters
# fittedposVel = data.frame(fittedposVel) %>% # forces the matrix to be a dataframe
#   rename(pos = V1)
#   
# # RILSetAnalysisScript.Rmd version
# # 2 - take last 10 points on that line
# sortedpos = sort(fittedposVel$pos, decreasing = TRUE)
# srtpos = sortedpos[1:10]
# final10Points = fittedposVel %>%
#   filter(pos >= srtpos)
# 
# # Calculate slope for each of these points
# final10REGR = REGR(final10Points$pos, 
#      res[[resValue]]$summary_table[2]$x0,	
#      res[[resValue]]$summary_table[3]$vf,	
#      res[[resValue]]$summary_table[4]$k,	
#      res[[resValue]]$summary_table[5]$n,
#      1)
# # Take -log(mean(x))
# logmeanFinalPos = -log(mean(final10REGR))
####################################################################################

# ####################################################################################
# # 1 December 2020
# # Defining the Maturation Zone: Finding points that are within the maturation zone
# ## This will help to see if roots with little/no mat zone should be removed from the data
# resValue = 3 # Used RIL40 as example
# pos = c(1:3000)
# # Get velocity fits for example data
# fittedVel = flf(pos, 
#                 res[[resValue]]$summary_table[2]$x0,	
#                 res[[resValue]]$summary_table[3]$vf,	
#                 res[[resValue]]$summary_table[4]$k,	
#                 res[[resValue]]$summary_table[5]$n)
# 
# # Get REGR fits for example data
# REGRtmp <- REGR(pos, 
#                   res[[resValue]]$summary_table[2]$x0,	
#                   res[[resValue]]$summary_table[3]$vf,	
#                   res[[resValue]]$summary_table[4]$k,	
#                   res[[resValue]]$summary_table[5]$n,
#                   1)
# 
# REGRfit = data.frame(cbind(pos, REGRtmp))
# maxREGR = max(REGRtmp) # finds Vmax
# per = 0.2 # percentage of area under the curve we want
# maxVel = max(fittedVel) # finds vf
# 
# velocityFit = data.frame(cbind(pos, fittedVel))
# plot(velocityFit)
# 
# ggplot(REGRfit, aes(x = pos)) +
#   geom_point(aes(y = REGRtmp))
# 
# # find values that are outside of 20% of the REGR curve, and also greater than 50% of the max velocity values = points in the maturation zone
# # Finds REGR points that are less than 20% of the max
# ## i.e. Draws line near bottom of REGR curve & grabs the points in meristematic & maturation zones
# # AND THEN
# # Finds Vel points that are greater than 50% of the max velocity
# ## BUT! reports the index number (row number) of the cases that are "true"
# ## i.e. Grabs the ~maturation~ part of the above selection
# k = which((REGRtmp < maxREGR*per) & (fittedVel > maxVel*0.5))
# k
# 
# # 12-01-2020 at 5:00pm w/ Nathan:
# # For every replicate: (AFTER THE FITTING, THIS IS SEPARATE)
# ## count number of rawData points fall within the maturation zone
# ## what % of points is that? -> distribution of this & find cut-off point
# 
# # 12-21-2020 Trying out the maturation zone defining now:
# # Now use that cut-off to count how many rawData points fall in the mat zone
# ## Then calc % of rawData points that fall in the mat zone
# ## Report out % of mat zone points w/ fileName
# 
# fittedVel[k]
# plot(pos[k], fittedVel[k], ylim = c(0, max(fittedVel[k])), xlim = c(0, 3000)) # just plots mat zone
# 
# minVelofMatZone = min(fittedVel[k]) # find min value of vel that's in mat zone
# 
# rawDatainMatZone = which(res[[3]]$rawData[[1]]$vel > minVelofMatZone)
# # Above won't work well, b/c no values are in the mat zone for RIL40...
# # Try again for RIL83 -> found values greater than mat zone start!
# percentofMatZone = (length(rawDatainMatZone)/length(res[[3]]$rawData[[1]]$vel))*100
# 
# fileName = rawData$fileName[1]
# fileName = str_split(fileName, '/', simplify = TRUE)[,8]
```

```{r plot-point-cloud-&-fitting, echo = FALSE}
# for loop to plot point cloud & fitted line on same graph
## Saves plot to Desktop/RILPop_plotsNEW/ for each replicate
## 12-07-2020
for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]])
    graphTitle = rawData$fileName[j]
    # Shorten fileName to the replicate name for simplicity
    # graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,8] #use for RILs
    graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,9] #use for IAA transport mutants
    print(graphTitle)
    fittedVel = flf(rawData$pos,
                    res[[i]]$summary_table$x0[j],
                    res[[i]]$summary_table$vf[j],
                    res[[i]]$summary_table$k[j],
                    res[[i]]$summary_table$n[j])
    
    print(ggplot(rawData, aes(x = rawData$pos)) +
      geom_point(aes(y = rawData$vel)) +
      geom_point(aes(y = fittedVel), color = "blue") +
      ggtitle(graphTitle) +
      xlab("Position from Root Tip (px)") +
      ylab("Velocity from Root Tip (px/frame)") +
      theme_bw())
    # Saving each graph as .tiff takes up more space than .pdf, so using .pdf for full RILSet
    # graphName = paste('~/Desktop/RILPop_plotsNEW/', graphTitle, "_", i, '_pointCloudFittedVel.pdf', sep = "")
    # graphName = paste('~/Desktop/pux1Imaging/pux1_plots/', graphTitle, '_pointCloudFittedVel.pdf', sep = "")
    graphName = paste('~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/IAAMutant_pointCloudFittedVel/', graphTitle, "_", i, '_pointCloudFittedVel.pdf', sep = "")
    # Saves plot to location written above ^
    ggsave(graphName)
  }
}

```

```{r percent-mat-zone, echo = FALSE}

### Thought process:
# which() gives the index of the velocity/REGR points that are in k
# this index won't work on pos values in the rawData, b/c there are 8000+ indices & the disk locations repeat along the root
# need to grab the velocity values at that point, graph them to see where they are & pull THOSE vel values from the rawData
## As of 11:51 on 12-21-2020 I did the above task, now to add it to a for loop!

## Calculating percent of Maturation Zone for each root
# Finished on 1-4-2021

percentofMatZone <- data.frame(filename = c(), percentofMatZone = c())

for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]]) 
    fileName = rawData$fileName[j]
    fileName = str_split(fileName, '/', simplify = TRUE)[,8]
    print(fileName)

    pos = c(1:3000)
    # Get velocity fits for example data
    fittedVel = flf(pos, 
                 res[[i]]$summary_table[2]$x0[j],	
                 res[[i]]$summary_table[3]$vf[j],	
                 res[[i]]$summary_table[4]$k[j],	
                 res[[i]]$summary_table[5]$n[j])

    # Get REGR fits for example data
    fittedREGR <- REGR(pos, 
                   res[[i]]$summary_table[2]$x0[j],	
                   res[[i]]$summary_table[3]$vf[j],	
                   res[[i]]$summary_table[4]$k[j],	
                   res[[i]]$summary_table[5]$n[j],
                   1)

    # REGRfit = data.frame(cbind(pos, fittedREGR))
    maxREGR = max(fittedREGR) # finds Vmax
    per = 0.2 # percentage of area under the curve we want
    maxVel = max(fittedVel) # finds vf

    velocityFit = data.frame(cbind(pos, fittedVel))
    # plot(velocityFit)

    # ggplot(REGRfit, aes(x = pos)) +
    #   geom_point(aes(y = fittedREGR))

    k = which((fittedREGR < maxREGR*per) & (fittedVel > maxVel*0.5)) # reports row number/column number of the cases that are "true"

    fittedVelofMatZone = fittedVel[k]
    # plot(pos[k], fittedVelofMatZone, ylim = c(0, max(fittedVelofMatZone)), xlim = c(0, 3000)) # just plots mat zone

    minVelofMatZone = min(fittedVelofMatZone) # find min value of vel that's in mat zone

    rawDatainMatZone = which(rawData$vel > minVelofMatZone)
    percentMatZone = (length(rawDatainMatZone)/length(res[[i]]$rawData[[j]]$vel))*100
    
    tmp <- data.frame(filename = fileName, percentofMatZone = percentMatZone)
    percentofMatZone <- rbind(percentofMatZone,tmp)
   
  }
  percentofMatZone
}

WholeRILSet_PercentofMatZone = percentofMatZone
# write.csv(WholeRILSet_PercentofMatZone, "~/Desktop/01-04-2021_WholeRILSet_PercentofMatZone.csv")
write.csv(WholeRILSet_PercentofMatZone, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/09-27-2021_IAAMutants_PercentofMatZone.csv")



WholeRILSet_PercentofMatZone = read.csv("~/Desktop/01-04-2021_WholeRILSet_PercentofMatZone.csv", header = TRUE) %>%
  select(-X)

ggplot(WholeRILSet_PercentofMatZone, aes(percentofMatZone)) +
  geom_density() +
  ggtitle("Percentages of Position Values that are in the Maturation Zone (Whole RIL Set)") +
  theme_bw()

rootsWithZeroMatZone = WholeRILSet_PercentofMatZone %>%
  filter(percentofMatZone < 0.0090)

rootswithLittleMatZone = WholeRILSet_PercentofMatZone %>%
  filter(percentofMatZone < 0.5)

# Note: there are 56 of 1631 roots that have 0 position points within the defined maturation zone
# Also Note: Visually, would like the cut-off to be 0.5% of the maturation zone included. Anything >5%, I'm comfy keeping. 
## I'll look into those <5%

#######################################################################################################################################
## As of 4pm 1-5-2021 Talked w/ Edgar, he said to check if there's a correlation b/w meanAbsDiff values & low % mat zone

### COMBINING DATAFRAMES
# Prep Summary Table of Parameters for plotting
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv") %>%
  select(-X) %>%
  group_by(fileName)

# Prep dataframe of percent of position points in mat zone & filenames for plotting
WholeRILSet_PercentofMatZone = read.csv("~/Desktop/01-04-2021_WholeRILSet_PercentofMatZone.csv", header = TRUE) %>%
  select(-X) %>%
  rename(fileName = filename) %>%
  group_by(fileName)
# Combine 2 dataframes above, keeps all fileName columns (they're identical), so no issue like I had with merge()
data = cbind(AllRILs_SummaryParameters, WholeRILSet_PercentofMatZone)
identical(data[['fileName']],data[['fileName1']]) # Yes, these are identical columns
write.csv(data, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILsSummaryParameters-withPercentMatZone.csv")

### PLOTTING
# Linear modeling to get slope/intercept for plot below
dataCrunch <- lm(percentofMatZone ~ meanAbsDiff, data) # Intercept = 6.103, meanAbsDiff = 57.211  
summary(dataCrunch)
# Plot percentMatZone vs meanAbsDiff
## Is there a correlation b/w high/low meanAbsDiff & % of points in mat zone -> Answer: Nope.
ggplot(AllRILs_SummaryParameters, aes(x = AllRILs_SummaryParameters$meanAbsDiff, y = WholeRILSet_PercentofMatZone$percentofMatZone)) +
  geom_point() +
  geom_abline(intercept = 6.103, slope = 57.211) +
  xlab("meanAbsDiff") +
  ylab("Percent of Pos Points in Maturation Zone") +
  ggtitle("") +
  theme_bw()

# Linear modeling for slope & intercept for plot below
dataCrunch2 <- lm(meanAbsDiff ~ percentofMatZone, data) # Intercept = 6.103, meanAbsDiff = 57.211  
summary(dataCrunch2)

# Same as above, but reversed axes
ggplot(WholeRILSet_PercentofMatZone, aes(x = WholeRILSet_PercentofMatZone$percentofMatZone, AllRILs_SummaryParameters$meanAbsDiff)) +
  geom_point() +
  geom_abline(intercept = 1.084e-01, slope = 3.241e-04) +
  xlab("Percent of Position Points in Maturation Zone") +
  ylab("Mean Absolute Difference") +
  ggtitle("") +
  theme_bw()

# There's no apparent correlation b/w meanAbsDiff and %ofMaturation Zone...

#######################################################################################################################################


### Create dataset that removes the 56 roots without mat zones
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv") %>%
  select(-X) %>%
  group_by(fileName)
data = cbind(AllRILs_SummaryParameters, WholeRILSet_PercentofMatZone)
identical(data[['fileName']], data[['fileName1']]) # Yes, these are identical columns
data = data.frame(data)
# Removes roots wth no maturation zone from dataset, leaving 1575 total roots
data = data %>%
  filter(percentofMatZone > 0.0)
# Write data to csv for later:
write.csv(data, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedNoMatZoneRoots.csv")


################################################################################
### Create dataset that removes 100 roots with few points in the mat zone
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv") %>%
  select(-X) %>%
  group_by(fileName)
data = cbind(AllRILs_SummaryParameters, WholeRILSet_PercentofMatZone)
identical(data[['fileName']],data[['fileName1']]) # Yes, these are identical columns
data = data.frame(data)
# Removes roots wth little (<0.5%) maturation zone from dataset, leaving 1497 total roots
data = data %>%
  filter(percentofMatZone > 0.5)
# Write data to csv for later:
write.csv(data, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedLittleMatZoneRoots.csv")
################################################################################
```


# Note: The following code chunks are copied from combineResStructures.Rmd to have one Analysis Script instead of several scripts doing partial work

```{r Load-Res-Structures}

######################################################################
# Note: only use this if your whole RILset is alone in the directory #
#### Else it'll combine all .RData files in the chosen directory! ####
######################################################################

# Iteratively loads in all res structures from ~/rildata directory by:
## Loads RData file into new environment
## Then extracts res variable
loadRData <- function(fileName) {
  #loads an RData file, and returns it
  e1 = new.env()
  load(fileName, e1)
  get("res", e1)
}
# 
# Load in correct res structure
# load("~/rildata/rildata_realfullDataset/2020_12_07_res_RILPop_full.RData")
# load("~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_res_pux1Day3.RData")
load("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-27_res_auxinMutants-withCol.RData")



# Pulls filenames from directory
# fils <- matrix(list.files("~/rildata/rildata_realfullDataset", pattern = "RData$", full.names = TRUE, recursive = TRUE))
# fils <- matrix(list.files("~/Desktop/pux1Imaging/pux1_Analysis/", pattern = "RData$", full.names = TRUE, recursive = TRUE))
fils <- matrix(list.files("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/", pattern = "RData$", full.names = TRUE, recursive = TRUE))


# # Loading them into RES structure
RES <- lapply(fils, loadRData)

# Shouldn't need this as of 11.19.2020  
## Use if combined multiple res structures
# save(RES, file = "~/rildata/rildata_fullDataset/2020_10_21_allresStructures.RData")
```

```{r Combine-Summary-Tables-of-Res-Structure}
############## function & for loop written on 30 January 2020 w/ Julian's help #############
####################### Copied from ParameterInvestigation.Rmd script ######################
# Function to separate res structure and rename pathname to filename for column "fileName" #
pathname_to_filename = function(genotype) {
  # Get genotype name from pathname
  genoName = basename(dirname(dirname(toString(genotype$fileName[[1]]))))
  # Create empty matrix of one column and as many rows as there are of res structure
  outnames = matrix(1, nrow(genotype))
  # outnames = matrix(1, as.numeric(nrow(genotype)))
  # Loops through each row of res
  ## Extracts pathname from each row in the dataframe
  ## Extracts filename from each pathname
  ## outnames = extracted filenames
  for (i in 1:nrow(genotype)) {
    namePlay_i  = toString(genotype$fileName[[i]])
    outnames[i] = basename(dirname(namePlay_i))
    print(outnames[i])
  }
  # Replaces pathname column with outnames column
  ## Now the column labeled "fileName" has filename instead of pathname
  genotype[["fileName"]] <- outnames
  # Return genotype summary table and genotype name
  gtype_gname = list(genotype, genoName)
  return(gtype_gname)
}

extractParameters = function(res) {
  # Create empty dataframe to fill with each RIL's parameters
  RILParameterSummaryTable = data.frame(matrix(
                                            ncol = 7, 
                                            nrow = 0, 
                                            dimnames = list(NULL, c("fileName", "x0", "vf", "k", "n", "meanAbsDiff", "matSlope"))))

  # for loop to call "pathname_to_filename" function for each genotype in res
  ## Fills dataframe with all replicates of all RILs' parameter summary tables
  for (i in 1:length(res)) {
    gtype = res[[i]]$summary_table
    gList = pathname_to_filename(gtype)
    summaryTable = gList[[1]]
    eval(parse(text = paste0(sprintf("%s = gList[[1]]", gList[[2]]))))
    RILParameterSummaryTable = rbind(RILParameterSummaryTable, summaryTable)
  }

  return(RILParameterSummaryTable)
}

# Uses function above to make summary table for parameters of all RILs
RILParams = lapply(RES, extractParameters)
RILParam_concatenated = bind_rows(RILParams)
# RILParam_concatenated = bind_rows(fileName) 

# Save progress
# write.csv(RILParam_concatenated, file = "~/rildata/rildata_realfullDataset/2020_12_07_RILsSummaryParameters.csv")
# write.csv(RILParam_concatenated, file = "~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_pux1Day3_SummaryParameters.csv")
write.csv(RILParam_concatenated, file = "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-27_IAAMutantsSummaryParameters-withCol.csv")


```

```{r shorten-fileName-to-be-RILnumbers}
# This code chunk creates a new column called "RILs" and fills that column with the shortened fileName
## This allows the RILs to be grouped together and averaged, because now they have the same name to be grouped
## Note: Revised on 2020-05-27 to add leading zeros before RIL number

# Start with file you just created (^), need to load() then get() to have in environment
# AllRILs_SummaryParameters = load("~/rildata/rildata_realfullDataset/2020_12_07_RILsSummaryParameters.csv")
# AllRILs_SummaryParameters = load("~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_pux1Day3_SummaryParameters.csv")
AllRILs_SummaryParameters = get(AllRILs_SummaryParameters)

AllRILs_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-27_IAAMutantsSummaryParameters-withCol.csv")


# Use if only need one RIL (how do you get select.r?)
# RIL1_SummaryParameters = AllRILs_SummaryParameters %>%
#   select.r(RIL1)


# Makes a column of shortened RIL names by copying the fileName column
## Make copy of fileName column called RILs
AllRILs_SummaryParameters$RILs <- AllRILs_SummaryParameters$fileName

# Extracts the "RIL##" from fileName and fills in the "RILs" column
## This works for RILs, but need to correct for Cvi & Ler
AllRILs_SummaryParameters$RILs <- str_extract(AllRILs_SummaryParameters$RILs, "[A-Z]+[0-9]+")
AllRILs_SummaryParameters$RILs = str_extract(AllRILs_SummaryParameters$RILs, "[0-9]+")


# Used this for IAA mutants data analysis
## Note: I changed the Col names to be col manually in Excel to make this part easier
AllRILs_SummaryParameters$mutants <- AllRILs_SummaryParameters$fileName
AllRILs_SummaryParameters$mutants <- str_extract(AllRILs_SummaryParameters$mutants, "[A-Z]*[a-z]*[0-9]*")


# # Used this for pux1 data analysis
# AllRILs_SummaryParameters$genotype <- AllRILs_SummaryParameters$fileName
# AllRILs_SummaryParameters$genotype = str_extract(AllRILs_SummaryParameters$genotype, "[^_]+")
# AllRILs_SummaryParameters$genotype = str_split(AllRILs_SummaryParameters$genotype, '--', simplify = TRUE)[,1]


#############################################################################################
######################## Use this chunk if need to add leading zeros ########################
#############################################################################################
# # Extract only number from RIL##
# AllRILs_SummaryParameters$RILs <- str_extract(AllRILs_SummaryParameters$RILs, "[0-9]+")
# 
# # Make numbers numeric instead of characters to use sprintf()
# AllRILs_SummaryParameters$RILs <- as.numeric(AllRILs_SummaryParameters$RILs)
# # Use sprintf() to add "RIL_" leadingzeros to 3 digits "# of RIL"
# AllRILs_SummaryParameters$RILs <- sprintf("RIL%03d", AllRILs_SummaryParameters$RILs)
# ##### Note: This works for RIL numbers, but messes up with Cvi & Ler
# 
# # Replace RIL0NA with NA
# AllRILs_SummaryParameters$RILs <- str_replace(AllRILs_SummaryParameters$RILs, "RIL0NA", replacement = NA_character_)
#############################################################################################

################################################################################################
##################### Use this if accidentally kept Cvi and Ler in dataset #####################
################################################################################################
# # Filter out NAs from the dataframe's RILs column (which are Cvi & Ler)
# ## Using string split(), and "--" as the separator
# ## Makes that output into a matrix (to index in next line)
# correctNAs = strsplit(AllRILs_SummaryParameters$fileName[is.na(AllRILs_SummaryParameters$RILs)], split = "--", fixed = TRUE)
# correctNAs = matrix(unlist(correctNAs), nrow = length(correctNAs), byrow = T)
# 
# # Takes column from above output that contains "Cvi" and "Ler" (this time it's 2nd column, hence correctNAs[,2])
# ## Replaces the NAs with "Cvi" and "Ler" strings
# AllRILs_SummaryParameters$RILs[is.na(AllRILs_SummaryParameters$RILs)] <- correctNAs[,2]


# Use if need to remove duplicate RILs
## Because the 1st code chunk loads one extra res file (Cvi, Ler & RILs1-10)
# AllRILs_SummaryParameters = AllRILs_SummaryParameters %>% 
#   distinct()


# Save progress in csv file
# write.csv(AllRILs_SummaryParameters, "~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv")
# write.csv(AllRILs_SummaryParameters, "~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_pux1Day3_SummaryParameters.csv")
write.csv(AllRILs_SummaryParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_IAAMutants_SummaryParameters-withCol.csv")

```

```{r sample-size-balancing}
##### This code chunk: Need to find RILs w/ 8+ samples & randomly reduce that to 8 #####

# Load in data saved from previous code chunk ^
# AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_07_AllRILs_SummaryParameters.csv")
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedLittleMatZoneRoots.csv")

# Variable for threshold of replicate numbers, may be used later so code is dynamic
# SAMPLETHRESH = 8

# Summary table subset that has column for RIL number and column for no. of replicates of that RIL no.
AllRILs_nParameters = AllRILs_SummaryParameters %>%
  # group_by(RILs) %>%
  group_by(mutants) %>%
  select(-X, -fileName) %>%
  tally() #%>%
  # filter(n >= SAMPLETHRESH)

# Save table with RIL & respective number of samples
write.csv(AllRILs_nParameters, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_nParameters-removedLittleMatZoneRoots.csv")
write.csv(AllRILs_nParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-01_IAAMutants_nParameters.csv")

#############################################################################################
################ Use this if need to level out sample numbers across dataset ################
#############################################################################################
# # Function to make data subset of RILs that have >5 replicates
# drawRILSamples = function(ril){
# 
#   # Takes in whole summary table of all RILs
#   rilSample = AllRILs_SummaryParameters %>% 
#     # Only filter out specified RIL replicates
#     ## "ril" in this case is a list of RILs that have >5 replicates (RILs2Sample below)
#     filter(RILs == ril)
#   # saves the RILs that have >8 replicates in data subset called randSample
#   randSample = sample_n(rilSample, SAMPLETHRESH)
#   # function output is data subset in randSample
#   return(randSample)
# }
# 
# # Creates list of RILs that are in the AllRILs_nParameters that have >8 replicates
# RILs2Sample = AllRILs_nParameters$RILs
# 
# # Uses drawRILSamples function to create data subset of randomly selected RILs from the list of RILs that contained >5 replicates
# subsetwCorrectedSampleSize = lapply(RILs2Sample, drawRILSamples) # right data (maybe?), wrong format
# # Fixed format of data subset with corrected replicate size
# subsetwCorrectedSampleSize = bind_rows(subsetwCorrectedSampleSize) # Ta daaaa
# 
# # Now make separate dataframe containing only RILs with <=5 replicates
# # Create list of RILs with okay relicate numbers
# subsetwFineSamples = AllRILs_SummaryParameters %>%
#   group_by(RILs) %>%
#   select(-X, -fileName) %>%
#   tally() %>%
#   filter(n < SAMPLETHRESH)
# 
# # Create data subset only containing RILs with correct number of replicates
# ## Will be binded with subset of data that just corrected replicate number
# subsetwFineSamples2 = AllRILs_SummaryParameters %>%
#   subset(RILs %in% subsetwFineSamples$RILs)
# 
# # The final dataframe containing corrected number of replicates for each RIL
# ## Please rename~~~~~~
# AllRILsCorrectedSampleSize = rbind(subsetwFineSamples2, subsetwCorrectedSampleSize) %>%
#   group_by(RILs) %>%
#   select(-X, -fileName)
# 
# # Save new dataset with corrected sample size (<= 5 samples) in csv file
# write.csv(AllRILsCorrectedSampleSize, "~/rildata/2020_08_23_AllRILs_CorrectedSampleSize_SummaryParameters.csv")

```

```{r parameter-distributions-all-roots}
# Taking a look at the distribution of parameters with new dataset that doesn't contain outliers (roots without a mat zone) nor RIL89 (too few samples)
data = read.csv("~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedNoMatZoneRoots.csv")
data = data %>%
  select(-X, -X.1)

# Note: k and n still very skewed left, will need to do log transformation & try again! (code for that is below)
ggplot(data, aes(n)) +
  geom_density()
ggplot(data, aes(k)) +
  geom_density()

ggplot(data, aes(vf)) +
  geom_density()

ggplot(data, aes(x0)) +
  geom_density()

```

```{r parameter-distributions-by-mutant}
# Outlier testing with density plots
# AllRILs_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_IAAMutants_SummaryParameters-withCol.csv")
# Now check without outliers
AllRILs_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_IAAMutants_SummaryParameters-withCol_outliersRemoved.csv")

  
# Make separate datasets for each mutant:
## abcb19
abcb19 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "abcb19")
## abcb4
abcb4 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "b4")
## pin2
pin2 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "pin2")
## Col-0 (WT)
Col = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "Col")

# Plot distribution plots of each parameter
dist_n = ggplot(pin2, aes(n)) +
  geom_density() +
  xlab("Parameter n for pin2") +
  theme_bw()

dist_k = ggplot(pin2, aes(k)) +
  geom_density() +
  xlab("Parameter k for pin2") +
  theme_bw()

dist_vf = ggplot(pin2, aes(vf)) +
  geom_density() +
  xlab("Parameter vf for pin2") +
  theme_bw()

dist_x0 = ggplot(pin2, aes(x0)) +
  geom_density() +
  xlab("Parameter x0 for pin2") +
  theme_bw()

# Plot all density plots on one page
parameterDensityPlots_pin2 = grid.arrange(dist_n, dist_k, dist_vf, dist_x0, 
             ncol = 2, nrow = 2)

```

# Notes on 20 (& 27) September 2021:

## Possible outliers as seen from density plots
* pin2--pin2_09--, x0 = -750 (definitely remove!)
* abcb19--abcb19_0uMIAA_02--, x0 = 264.2016
* Col--Col_0uMIAA_04--, x0 = 284.2808
* Col--Col_0uMIAA_12--, x0 = 208.9013

## Also, consider doing a log transformations on n and k (to keep with RIL processing)

```{r parameter-boxplots}
# Outlier Testing with Boxplots:
## Note: Manually change which genotype you're plotting!

# Do this again to check boxplots after outlier removal (done on 27 Sept 2021)
AllRILs_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_IAAMutants_SummaryParameters-withCol_outliersRemoved.csv")

abcb19 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "abcb19")
## abcb4
abcb4 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "b4")
## pin2
pin2 = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "pin2")
## Col-0 (WT)
Col = AllRILs_SummaryParameters %>%
  select(-X1) %>%
  filter(AllRILs_SummaryParameters$mutants == "Col")

boxplot_x0 = ggplot(pin2) +
  aes(x = "", y = x0) +
  geom_boxplot(fill = "blue") +
  xlab("pin2") + 
  theme_bw()

boxplot_vf = ggplot(pin2) +
  aes(x = "", y = vf) +
  geom_boxplot(fill = "red") +
  xlab("pin2") + 
  theme_bw()

boxplot_k = ggplot(pin2) +
  aes(x = "", y = k) +
  geom_boxplot(fill = "green") +
  xlab("pin2") + 
  theme_bw()

boxplot_n = ggplot(pin2) +
  aes(x = "", y = n) +
  geom_boxplot(fill = "orange") +
  xlab("pin2") + 
  theme_bw()

# Plot all four boxplots on one page, as done in last code chunk
parameterBoxplots = grid.arrange(boxplot_n, boxplot_k, boxplot_vf, boxplot_x0, 
             ncol = 2, nrow = 2)

# Now manually remove outliers that were dots on the boxplots! - done on 27 Sept 2021

## Outlier Testing from Stuti (use this!)
check_outliers(dataframe, specifics)

# Plot bar graphs of parameters
data = AllRILs_SummaryParameters %>%
  select(-X1, -fileName, -meanAbsDiff, -matSlope)
# Melt data to be long format for easy ggplot graphing
data_long = melt(data, ID.vars = "mutants")
# Separate out dataset by parameters
data_x0 = data_long %>%
  filter(variable == "x0")
data_vf = data_long %>%
  filter(variable == "vf")
data_k = data_long %>%
  filter(variable == "k")
data_n = data_long %>%
  filter(variable == "n")

# Now plot
ggplot(data_x0, aes(x = mutants)) +
  geom_bar(aes(y = value))
  
ggplot(data_long, aes(mutants, value)) +   
  geom_bar(aes(fill = variable), position = "dodge", stat="identity")
```

```{r log(Parameter)-stats-by-RIL}
# This code chunk is to average parameters per RIL to create a table for the input of the R/qtl2 package
## Uses output from previous code chunk "shorten-fileName-to-be-RILnumbers"
# Info needed from RILs:
log() # take log() of all parameters to make data more normal
mean() # average of that RIL's parameter -> won't use this b/c have non-normal data
median() # median of that RIL's parameter -> WILL use this b/c have non-normal data
sd() # st dev of that RIL's parameter
var() # variance of that RIL's parameter
tally() # No. of samples for each RIL

# Load in csv with data
# AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_SummaryParameters-removedNoMatZoneRoots.csv")
# AllRILs_SummaryParameters = read.csv("~/Desktop/pux1Imaging/pux1_Analysis/2020_12_08_pux1Day3_SummaryParameters.csv")
# AllRILs_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021-09-27_IAAMutants_SummaryParameters.csv")
AllRILs_SummaryParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2021-11-22_res_auxinMutants_SummaryParameters-wCol.csv")


# Take log of all parameters to produce more normal data
AllRILs_logParameters = AllRILs_SummaryParameters %>%
  # group_by(RILs) %>%
  # select(-X, -fileName, -mle) %>%
  # log(a,b) b = base for log, else R will calc ln()
  mutate(logK = log(AllRILs_SummaryParameters$k, 10)) %>%
  # mutate(logX0 = log(AllRILs_SummaryParameters$x0, 10)) %>%
  mutate(logN = log(AllRILs_SummaryParameters$n, 10)) #%>%
  # mutate(RIL = as.numeric(RILs))

## Group by RIL to group together & get stats for each RIL (not taking stat of whole pop)
## Removed X (rownames created from csv) and fileName column from dataframe
## Calc'd chosen stat via summarise_each(funs())
## PLEASE NOTE: mutate(RIL = as.numeric(RILs)) JUST NAMES THE RILS AS 1-162, WITHOUT RECOGNIZING WHICH RIL ITS COVERING!!!
### EXAMPLE: RIL10 = RIL2 B/C ITS THE 2ND RIL AFTER RIL1 IN THE "RILs" COLUMN!!! i.e. don't use this, unless you can fix it!

# AllRILs_AveragedParameters = AllRILs_logParameters %>%
AllRILs_AveragedParameters = AllRILs_SummaryParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(mutants) %>%
  # group_by(RILs) %>%
  # group_by(genotype) %>% 
  select(-fileName,) %>%
  # select(-X1, -fileName, -matSlope, -meanAbsDiff) %>%
  # select(-X, -fileName, -matSlope, -meanAbsDiff) %>% # Use if want to remove fitting metrics from dataset
  summarise_each(funs(mean(., na.rm = TRUE))) # Added na.rm so that averages didn't calc in the NAs for the mean

# AllRILs_MedianParameters = AllRILs_logParameters %>%
AllRILs_MedianParameters = AllRILs_SummaryParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>%
  # group_by(genotype) %>%
  select(-fileName, -X, -fileName1) %>%
  summarise_each(funs(median))

# AllRILs_StDevParameters = AllRILs_logParameters %>%
AllRILs_StDevParameters = AllRILs_SummaryParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>%
  # group_by(genotype) %>%
  select(-X, -fileName, -fileName1) %>%
  summarise_each(funs(sd)) 

# AllRILs_VarianceParameters = AllRILs_logParameters %>%
AllRILs_VarianceParameters = AllRILs_SummaryParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>%
  # group_by(genotype) %>%
  select(-X, -fileName, -fileName1) %>%
  summarise_each(funs(var))

# AllRILs_nParameters = AllRILs_logParameters %>%
#   # mutate(RIL = as.numeric(RILs)) %>%
#   group_by(RILs) %>%
#   # select(-X, -fileName) %>%
#   tally()

# Save all files from above
# write.csv(AllRILs_AveragedParameters, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_AveragedParameters-removedLittleMatZoneRoots.csv")
write.csv(AllRILs_AveragedParameters, "~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2021_11_23_AllMutants_AveragedParameters.csv")
write.csv(AllRILs_MedianParameters, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_MedianParameters-removedLittleMatZoneRoots.csv")
write.csv(AllRILs_StDevParameters, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_StDevParameters-removedLittleMatZoneRoots.csv")
write.csv(AllRILs_VarianceParameters, "~/rildata/rildata_realfullDataset/2021_01_07_AllRILs_VarianceParameters-removedLittleMatZoneRoots.csv")
# write.csv(AllRILs_nParameters, "~/rildata/rildata_fullDataset/2020_10_08_AllRILs_nParameters.csv")


```

```{r ttests-for-mutant-parameters}
# t-tests for x0 parameter
qqplot(abcb19_3$x0, runif(1000)) # ran for Col, pin2, abcb4, & abcb19 (all mostly follow a N dist)
x0_Col_pin2 = t.test(Col$x0, pin2$x0, var.equal = FALSE) # p-value = 0.0003622
x0_Col_abcb4 = t.test(Col$x0, abcb4$x0, var.equal = FALSE) # p-value = 0.1143
x0_Col_abcb19 = t.test(Col$x0, abcb19$x0, var.equal = FALSE) # p-value = 0.002635

# t-tests for vf parameter
qqplot(pin2$vf, runif(1000)) # ran for Col, pin2, abcb4, & abcb19 (Col & pin2 follows N dist, b4 & 19 don't)
vf_Col_pin2 = t.test(Col$vf, pin2$vf, var.equal = FALSE) # p-value = 0.3982
vf_Col_abcb4 = t.test(Col$vf, abcb4$vf, var.equal = FALSE) # p-value = 0.3621
vf_Col_abcb19 = t.test(Col$vf, abcb19$vf, var.equal = FALSE) # p-value = 0.9672

# t-tests for k parameter
qqplot(abcb19$k, runif(1000)) # ran for Col, pin2, abcb4, & abcb19 (Col & pin2 follows N dist, b4 & 19 don't)
k_Col_pin2 = t.test(Col$k, pin2$k, var.equal = FALSE) # p-value = 0.004529
k_Col_abcb4 = t.test(Col$k, abcb4$k, var.equal = FALSE) # p-value = 0.001273
k_Col_abcb19 = t.test(Col$k, abcb19$k, var.equal = FALSE) # p-value = 0.00362

# t-tests for n parameter
qqplot(pin2$n, runif(1000)) # ran for Col, pin2, abcb4, & abcb19 (all mostly follow a N dist)
n_Col_pin2 = t.test(Col$n, pin2$n, var.equal = FALSE) # p-value = 0.7852
n_Col_abcb4 = t.test(Col$n, abcb4$n, var.equal = FALSE) # p-value = 0.01829
n_Col_abcb19 = t.test(Col$n, abcb19$n, var.equal = FALSE) # p-value = 0.0008324

# Compare pin2 (upwards IAA flow) vs other mutants
t.test(pin2$x0, abcb4$x0, var.equal = FALSE) # p-value = 0.003895
t.test(pin2$x0, abcb19$x0, var.equal = FALSE) # p-value = 4.639e-06
t.test(pin2$vf, abcb4$vf, var.equal = FALSE) # p-value = 0.9406
t.test(pin2$vf, abcb19$vf, var.equal = FALSE) # p-value = 0.4366
t.test(pin2$k, abcb4$k, var.equal = FALSE) # p-value = 0.4177
t.test(pin2$k, abcb19$k, var.equal = FALSE) # p-value = 0.8304
t.test(pin2$n, abcb4$n, var.equal = FALSE) # p-value = 0.05586
t.test(pin2$n, abcb19$n, var.equal = FALSE) # p-value = 0.001411

# Compare abcb4 (upwards IAA flow) vs abcb19 (downwards IAA flow)
t.test(abcb4$x0, abcb19$x0, var.equal = FALSE) # p-value = 0.0001215
t.test(abcb4$vf, abcb19$vf, var.equal = FALSE) # p-value = 0.4018
t.test(abcb4$k, abcb19$k, var.equal = FALSE) # p-value = 0.3253
t.test(abcb4$n, abcb19$n, var.equal = FALSE) # p-value = 0.0175


ggplot()
```

```{r brief-outlier-testing}
# install.packages("outliers")
library(outliers)
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_fullDataset/2020_10_08_AllRILs_SummaryParameters.csv")

AllRILs_SummaryParameters = AllRILs_SummaryParameters %>%
  select(-X, -fileName) %>%
  group_by(RILs)

parametersMelted = melt(AllRILs_logParameters, id.var = "RILs")

# Boxplot to Visualize parameter distribution
ggplot(data = parametersMelted, aes(x = variable, y = value)) + 
  geom_boxplot(aes(fill = variable)) +
  ylab("") +
  xlab("Parameters") +
  ggtitle("Distribution of Parameters for Whole RIL Population") +
  theme_bw() +
  facet_wrap( ~ variable, scales = "free")

# Historgram of Parameters (FULL dataset)
ggplot(AllRILs_logParameters) +
  aes(x = x0) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = vf) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = logK) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = logN) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()


# Do distribution curves for each parameter in full dataset!
################# 2020_10_13 #################
## Overlying histogram & density plots
x0_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = x0)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=30,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(x0, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for x0 for Whole RIL Population") +
  theme_bw()

vf_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = vf)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=.3, # Change binwidth to match data (ex: x0 mean is ~300, need binwidth=30)
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(vf, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for vf for Whole RIL Population") +
  theme_bw()

logK_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = logK)) +
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=0.05,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(logK, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for logK for Whole RIL Population") +
  theme_bw()

logN_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = logN)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=0.1,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(logN, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for logN for Whole RIL Population") +
  theme_bw()




# Testing outliers using chisq test from the Outliers Package in R
## Should I divide these up by RILs and then by phenotype?
chisq.out.test(AllRILs_SummaryParameters$x0, variance=var(AllRILs_SummaryParameters$x0), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$x0, variance=var(AllRILs_SummaryParameters$x0), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$vf, variance=var(AllRILs_SummaryParameters$vf), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$vf, variance=var(AllRILs_SummaryParameters$vf), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$k, variance=var(AllRILs_SummaryParameters$k), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$k, variance=var(AllRILs_SummaryParameters$k), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$n, variance=var(AllRILs_SummaryParameters$n), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$n, variance=var(AllRILs_SummaryParameters$n), opposite = TRUE) # TRUE=highest value

```

```{r fittingVelCurves}
### Creates numeric vector for means of the parameters ###
### Makes range of y from 0.0 to 3.5 px/hr ###
### pos values range from 0-2000 px from QC, increasing by 1 px at a time ###
ku         <- vector('numeric')
range_of_y <- range(0, 3.5)
pos        <- seq(0, 2000, 1)

```

```{r EvaluateVelandREGRFits}
# Note: This code chunk is copied from AnalyzeKinematic[...].Rmd
# Loops through all genotypes/conditions evaluating the equation at a 
## value, Pos (fixed position values (0-2000, increments of 1)), to 
## calculate velocity and REGR values using the maximum likelihood 
## estimate parameters for each replicate
# WARNING: Fits ALL replicates, not the average. To fit the avg vel, 
## look to the next code chunk
# Please Note: The final product has the correct units (hallelujah!)
for (i in 1:length(res)) {
  resultVel <- evaluateVelFits(res[[i]], pos)
  matrixEnd = ncol(resultVel) - 1
  for (j in 2:matrixEnd) {
    resultVel[,j] <- as.numeric(resultVel[,j])} # without unit conversion
  resultVel[,1] = as.numeric(resultVel[,1]) # without unit conversion
  #   resultVel[,j] <- as.numeric(resultVel[,j]) * 0.08 } # conversion from px/frame to mm/hr for all velocity value columns
  # resultVel[,1] = as.numeric(resultVel[,1]) / 1500 # conversion from px to mm for the one position value column
  write.csv(resultVel, paste('/Users/ashleyhenry/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/PosEvaluatedVel', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultVel[,1], resultVel[,2])
  
  ######################################
  
  # resultREGR <- evaluateREGRFits(res[[i]], pos, 120*100)
  resultREGR <- evaluateREGRFits(res[[i]], pos, 1) #without unit conversion
  matrixEnd = ncol(resultREGR) - 1
  
  # for (k in 2:matrixEnd) {
    # resultREGR[,j] <- as.numeric(resultREGR[,j]) * 120} # DOESN'T WORK: conversion from px/frame*frame to px/frame*hr (or %/hr) for all velocity value columns
  
  # resultREGR[,1] = as.numeric(resultREGR[,1]) / 1500 # WORKS: conversion from px to mm for the one position value column
  resultREGR[,1] = as.numeric(resultREGR[,1]) # without unit conversion
  write.csv(resultREGR, paste('/Users/ashleyhenry/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles//PosEvaluatedREGR', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultREGR[,1], resultREGR[,2])
}
```

```{r evaluating-x0-bc-Nathan-said-so}
# 7 October 2021
# Seeing if x0 relates to 1/2Vmax
AllRILs_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_IAAMutants_SummaryParameters-withCol_outliersRemoved.csv")

data = AllRILs_SummaryParameters[25,]
pos <- seq(0, 2000, 1)
flfPlot = flf(pos, 
              AllRILs_SummaryParameters[25,]$x0, 
              AllRILs_SummaryParameters[25,]$vf, 
              AllRILs_SummaryParameters[25,]$k, 
              AllRILs_SummaryParameters[25,]$n)
plotMe = cbind(pos, flfPlot)
plotMe = data.frame(plotMe)

ggplot(plotMe, aes(x = pos)) +
  geom_point(y = flfPlot) +
  ylim(0, 1.5) +
  xlim(0, 2000) +
  theme_bw()

Evalx0 = flf(AllRILs_SummaryParameters[25,]$x0,
              AllRILs_SummaryParameters[25,]$x0, 
              AllRILs_SummaryParameters[25,]$vf, 
              AllRILs_SummaryParameters[25,]$k, 
              AllRILs_SummaryParameters[25,]$n)

# Checked that Morris & Silk 1992, Equation 7 is true with my data
## Note: It is & we can continue this work (whew)
# leftSideofEq7 = Evalx0^AllRILs_SummaryParameters[25,]$n
# rightSideofEq7 = AllRILs_SummaryParameters[25,]$vf^AllRILs_SummaryParameters[25,]$n
# rightRealSideofEq7 = rightSideofEq7/2
```

```{r changing-x0-if-sig-different}
# 7 October 2021
# avg parameters for Col
AuxinMutants_AveragedParameters = read.csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_AllMutants_AveragedParameters-outliersRemoved.csv")
AuxinMutants_AveragedParameters_Col = AuxinMutants_AveragedParameters[3,]
# avg parameters for pin2
AuxinMutants_AveragedParameters_pin2 = AuxinMutants_AveragedParameters[4,]
# avg parameters for abcb19
AuxinMutants_AveragedParameters_abcb19 = AuxinMutants_AveragedParameters[1,]
# Plot avg Col vel curves
pos <- seq(0, 2000, 1)
velCurve_Col = flf(pos, 
              AuxinMutants_AveragedParameters_Col$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_Col$k, 
              AuxinMutants_AveragedParameters_Col$n)
# Plot vel with Col vf, k, & n and w/ pin2 x0
velCurve_pin2 = flf(pos, 
              AuxinMutants_AveragedParameters_pin2$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_pin2$k, 
              AuxinMutants_AveragedParameters_Col$n)
# Plot vel with Col vf, k, & n and w/ abcb19 x0
velCurve_abcb19 = flf(pos, 
              AuxinMutants_AveragedParameters_abcb19$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_abcb19$k, 
              AuxinMutants_AveragedParameters_Col$n)
# Plot vel for all
allData = cbind(pos, velCurve_Col, velCurve_pin2, velCurve_abcb19)
allData = data.frame(allData)
ggplot(allData, aes(x = pos)) +
  geom_point(y = velCurve_Col, color = "black") +
  geom_point(y = velCurve_abcb19, color = "red") +
  geom_point(y = velCurve_pin2, color = "blue") +
  ylim(0, 1.75) +
  xlim(0, 2000) +
  ggtitle("Switched x0 & k, abcb19 = red, pin2 = blue, Col = black") +
  xlab("Position from Quiescent Center (px)") +
  ylab("Velocity (px/frame)") +
  theme_bw()
  
# Now the same as above, but with REGR curves
# Plot avg Col REGR curves
pos <- seq(0, 2000, 1)
REGRCurve_Col = REGR(pos, 
              AuxinMutants_AveragedParameters_Col$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_Col$k, 
              AuxinMutants_AveragedParameters_Col$n,
              1)
# Plot REGR with Col vf, k, & n and w/ pin2 x0
REGRCurve_pin2 = REGR(pos, 
              AuxinMutants_AveragedParameters_pin2$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_pin2$k, 
              AuxinMutants_AveragedParameters_Col$n,
              1)
# Plot REGR with Col vf, k, & n and w/ abcb19 x0
REGRCurve_abcb19 = REGR(pos, 
              AuxinMutants_AveragedParameters_abcb19$x0, 
              AuxinMutants_AveragedParameters_Col$vf, 
              AuxinMutants_AveragedParameters_abcb19$k, 
              AuxinMutants_AveragedParameters_Col$n,
              1)
# Plot all
allData = cbind(pos, REGRCurve_Col, REGRCurve_pin2, REGRCurve_abcb19)
allData = data.frame(allData)
ggplot(allData, aes(x = pos)) +
  geom_point(y = REGRCurve_Col, color = "black") +
  geom_point(y = REGRCurve_abcb19, color = "red") +
  geom_point(y = REGRCurve_pin2, color = "blue") +
  ylim(0, 0.0035) +
  xlim(0, 2000) +
  ggtitle("Switched x0 & k, abcb19 = red, pin2 = blue, Col = black") +
  xlab("Position from Quiescent Center (px)") +
  ylab("Velocity (px/frame)") +
  theme_bw()
```

```{r long-way-plotting-IAA-Mutants}
Cvi_vel = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_Cvi.csv")
Ler_vel = read_csv("/Users/ashleyhenry/Desktop/avgVelCurve_Ler.csv")

Cvi_vel = Cvi_vel %>%
  rename(
    "Pos" = V1,
    "Cvi_vel" = V2
  )

Ler_vel = Ler_vel %>%
  rename(
    "Pos" = V1,
    "Ler_vel" = V2
  )


# Change units from px/frame -> mm/hr
Cvi_vel$Pos = Cvi_vel$Pos/1500
Cvi_vel$Cvi_vel = Cvi_vel$Cvi_vel*0.08202

Ler_vel$Pos = Ler_vel$Pos/1500
Ler_vel$Ler_vel = Ler_vel$Ler_vel*0.08202

# Save new file with correct units (mm & mm/hr) (!!!)
write.csv(Cvi_vel, paste('/Users/ashleyhenry/Desktop/avgVelCurve_Cvi_CORRECTUNITS.csv'), row.names = F)
write.csv(Ler_vel, paste('/Users/ashleyhenry/Desktop/avgVelCurve_Ler_CORRECTUNITS.csv'), row.names = F)

# Add dataset by dataset to make full dataset of Cvi & Ler for 2018 & 2019
CviLer_vel = merge(Cvi_vel,
               Ler_vel,
               by = "Pos")
  
# Make merged dataset into long format
CviLer_vel_LongFormat = melt(CviLer_vel, id.var = "Pos")

# Graph data from above^
ggplot(CviLer_vel_LongFormat, aes(x = Pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Quiescent Center (mm)") +
  ylab("Velocity from Root Tip (mm/hr)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi & Ler") +
  theme_bw()

## Now to write a short way of plotting all IAA mutants
avgParameters_Mutants = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_AllMutants_AveragedParameters-outliersRemoved.csv")

```

```{r short-way-of-plotting}
### Creates numeric vector for means of the parameters ###
### Makes range of y from 0.0 to 3.5 px/hr ###
### pos values range from 0-2000 px from QC, increasing by 1 px at a time ###
ku         <- vector('numeric')
range_of_y <- range(0, 3.5)
pos        <- seq(0, 2000, 1)

flfPlot = flf(pos, avgParameters_Mutants$x0[1], avgParameters_Mutants$vf[1], avgParameters_Mutants$k[1], avgParameters_Mutants$n[1])

# Matrix that has position values in 1st column and fitted velocity values in 2nd column
# "abcb19" "b4"     "Col"    "pin2" 
avgVelCurve <- matrix(nrow = length(pos), ncol = 6)
avgVelCurve[,1] <- pos
avgVelCurve[,2] <- flf(pos, AllRILs_AveragedParameters$x0[1], AllRILs_AveragedParameters$vf[1], AllRILs_AveragedParameters$k[1], AllRILs_AveragedParameters$n[1]) 
avgVelCurve[,3] <- flf(pos, AllRILs_AveragedParameters$x0[2], AllRILs_AveragedParameters$vf[2], AllRILs_AveragedParameters$k[2], AllRILs_AveragedParameters$n[2])
avgVelCurve[,4] <- flf(pos, AllRILs_AveragedParameters$x0[3], AllRILs_AveragedParameters$vf[3], AllRILs_AveragedParameters$k[3], AllRILs_AveragedParameters$n[3])
avgVelCurve[,5] <- flf(pos, AllRILs_AveragedParameters$x0[4], AllRILs_AveragedParameters$vf[4], AllRILs_AveragedParameters$k[4], AllRILs_AveragedParameters$n[4])
avgVelCurve[,6] <- flf(pos, AllRILs_AveragedParameters$x0[5], AllRILs_AveragedParameters$vf[5], AllRILs_AveragedParameters$k[5], AllRILs_AveragedParameters$n[5])

# Make a dataframe
avgVelCurve = data.frame(avgVelCurve)
# Change column names to pos & genotype
colnames(avgVelCurve) <- c("pos", "abcb19-3", "abcb4-1", "abcb4-2", "abcb4-3", "Col")
# Turn to long format
avgVelCurve_IAAMutants_longForm = melt(avgVelCurve, id.var = "pos")
# Save work
write.csv(avgVelCurve, paste('/Users/ashleyhenry/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2021-11-23_avgVelCurve_IAAMutants-wAlleles-wCol.csv'), row.names = F)

# Plot this
ggplot(avgVelCurve_IAAMutants_longForm, aes(x = pos, y = value, color = variable)) +
  geom_point() +
  # ylim(0, 3.5) +
  xlab("Position from Quiescent Center (px)") +
  ylab("Velocity from Root Tip (px/frame)") +
  # ggtitle("Relative Elemental Growth Rate for Cvi & Ler") +
  theme_bw()

# This doesn't work well...
# REGR is giving funny values, 
REGRPlot = REGR(pos, avgParameters_Mutants$x0[1], avgParameters_Mutants$vf[1], avgParameters_Mutants$k[1], avgParameters_Mutants$n[1], 1500)

# We're calculating the derivative of flf to see if we get the same values as our REGR process
grad(avgVelCurve[,2])

fwdDiff <- function(x) {
  fx1 <- flf(x+1, )
  fx <- flf(x)
  return(fx1-fx)
}

grad_out <- grad(fwdDiff, angleCurve[,2])


```

```{r plotting-vel-curves-IAA-mutants}
AllRILs_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData/2021_09_27_AllMutants_AveragedParameters-outliersRemoved.csv")
# In the averaged csv:
## 1 = abcb19
## 2 = abcb4
## 3 = Col
## 4 = pin2

pos <- seq(0, 2000, 1)
velCurve_abcb19 = flf(pos,
                      AllRILs_SummaryParameters[1,]$x0,
                      AllRILs_SummaryParameters[1,]$vf,
                      AllRILs_SummaryParameters[1,]$k,
                      AllRILs_SummaryParameters[1,]$n)
velCurve_abcb4 = flf(pos,
                     AllRILs_SummaryParameters[2,]$x0,
                     AllRILs_SummaryParameters[2,]$vf,
                     AllRILs_SummaryParameters[2,]$k,
                     AllRILs_SummaryParameters[2,]$n)
velCurve_Col = flf(pos,
                   AllRILs_SummaryParameters[3,]$x0,
                   AllRILs_SummaryParameters[3,]$vf,
                   AllRILs_SummaryParameters[3,]$k,
                   AllRILs_SummaryParameters[3,]$n)
velCurve_pin2 = flf(pos,
                    AllRILs_SummaryParameters[4,]$x0,
                    AllRILs_SummaryParameters[4,]$vf,
                    AllRILs_SummaryParameters[4,]$k,
                    AllRILs_SummaryParameters[4,]$n)
velCurves = cbind(pos, velCurve_abcb19, velCurve_abcb4, velCurve_Col, velCurve_pin2)
velCurves = data.frame(velCurves)

velCurves_long = melt(velCurves, id.vars = "pos")

ggplot(velCurves_long, aes(x = pos, y = value, color = variable)) +
  geom_point() +
  ylim(0, 1.5) +
  xlim(0, 2000) +
  xlab("Position from Quiescent Center (px)") +
  ylab("Velocity from QC (px/frame)") +
  ggtitle("Velocity Curves for Auxin Transport Mutants") +
  theme_bw()
```

```{r plotting-REGR-curves-IAA-mutants}
AllRILs_SummaryParameters = read_csv("~/Desktop/AuxinTransportMutants/2020-21_Data/IAAMutants_ProcessedData-wAlleles/2021-11-22_res_auxinMutants_SummaryParameters-wCol.csv")
# In the averaged csv:
## 1 = abcb19
## 2 = abcb4
## 3 = Col
## 4 = pin2

pos <- seq(0, 2000, 1)
REGRCurve_abcb19_3 = REGR(pos,
                      AllRILs_SummaryParameters[1,]$x0,
                      AllRILs_SummaryParameters[1,]$vf,
                      AllRILs_SummaryParameters[1,]$k,
                      AllRILs_SummaryParameters[1,]$n,
                      1)
REGRCurve_abcb4_1 = REGR(pos,
                     AllRILs_SummaryParameters[2,]$x0,
                     AllRILs_SummaryParameters[2,]$vf,
                     AllRILs_SummaryParameters[2,]$k,
                     AllRILs_SummaryParameters[2,]$n,
                      1)
REGRCurve_abcb4_2 = REGR(pos,
                   AllRILs_SummaryParameters[3,]$x0,
                   AllRILs_SummaryParameters[3,]$vf,
                   AllRILs_SummaryParameters[3,]$k,
                   AllRILs_SummaryParameters[3,]$n,
                      1)
REGRCurve_abcb4_3 = REGR(pos,
                    AllRILs_SummaryParameters[4,]$x0,
                    AllRILs_SummaryParameters[4,]$vf,
                    AllRILs_SummaryParameters[4,]$k,
                    AllRILs_SummaryParameters[4,]$n,
                      1)
REGRCurve_Col = REGR(pos,
                    AllRILs_SummaryParameters[5,]$x0,
                    AllRILs_SummaryParameters[5,]$vf,
                    AllRILs_SummaryParameters[5,]$k,
                    AllRILs_SummaryParameters[5,]$n,
                      1)

REGRCurves = cbind(pos, REGRCurve_abcb19_3, REGRCurve_abcb4_1, REGRCurve_abcb4_2, REGRCurve_abcb4_3, REGRCurve_Col)
REGRCurves = data.frame(REGRCurves)

REGRCurves_long = melt(REGRCurves, id.vars = "pos")

ggplot(REGRCurves_long, aes(x = pos, y = value, color = variable)) +
  geom_point() +
  ylim(0, 0.004) +
  xlim(0, 2000) +
  xlab("Position from Quiescent Center (px)") +
  ylab("Relative Elemental Growth Rate from QC (%/hr)") +
  ggtitle("REGR Curves for Auxin Transport Mutants") +
  theme_bw()
```


