---
title: "RIL Set Analysis Script"
author: "Ashley Henry"
date: "4/9/2020"
output: html_document
---

```{r setup, include=FALSE}
### Gets flf package loaded into environment ###
# install.packages("backports")
# install.packages("rcmdcheck")
# install.packages("devtools")
# install.packages("rowr")
# install.packages("plotly")
# install.packages("naniar")
# setwd("/Users/ashleyhenry/")
devtools::load_all('/Users/ashleyhenry/flf')
library(flf)
library(ggplot2)
library(plotly)
library(tidyverse)
library(readr)
library(rowr)
require(reshape2)
library(dplyr)
library(naniar)
library(neldermead)
```

# Script to Analyze RIL Set
__Note:__ 

## Script Completions:
* Loads in all clicking data into a res structure (complicated list of lists)
* Combines all res structures into one workable dataframe
* Relabels data as simplified RIL name (not path/filename)
* Balances out sample size (currently at less than/equal to 8 replicates)
* Calculates log(k) and log(n)
* Calculates average, median, st dev, & variance of the parameters for each RIL

## Script to-dos:
* Repeatable & efficient outlier testing (one-by one version in AnalyzeKinematic[...].Rmd)
* Velocity curves (calcs pos & vel from parameters)
* Goodness of fit for flf curve (R^2, show flf on point cloud for each RIL)
* REGR curves (calc pos & REGR from parameters)
* 

```{r load-data, echo=FALSE}
### Below is copied from AnalyzeKinematicAnalysisToolOutput.Rmd
### Creates path with folder of folders, each with one rawData.csv file
### Loads in all of the rawData.csv files ###
masterPath <- "~/Desktop/RILPop_tmp/"
# masterPath <- "~/Desktop/pux1Imaging/Day3_pux1Clicked"

# devtools::load_all('/Users/ashleyhenry/flf')
# library(flf)

# 11-23-2020
# loopValue = number of times I'm taking 90% of the data with the lowest residuals
# loopValue at ~6 for those with high mle
res <- processMasterFolder(masterPath, 1)

####################################################################
# for loop to plot point cloud & fitted line on same graph
# Saves plot to Desktop for each replicate
## 12-07-2020
for (i in 1:length(res)){
  for(j in 1:length(res[[i]]$rawData)){
    rawData <- as.data.frame(res[[i]]$rawData[[j]])
    graphTitle = rawData$fileName[j]
    # Shorten fileName to the replicate name for simplicity
    graphTitle = str_split(graphTitle, '/', simplify = TRUE)[,8]
    print(graphTitle)
    fittedVel = flf(rawData$pos,
                    res[[i]]$summary_table$x0[j],
                    res[[i]]$summary_table$vf[j],
                    res[[i]]$summary_table$k[j],
                    res[[i]]$summary_table$n[j])
    
    print(ggplot(rawData, aes(x = rawData$pos)) +
      geom_point(aes(y = rawData$vel)) +
      geom_point(aes(y = fittedVel), color = "blue") +
      ggtitle(graphTitle) +
      xlab("Position from Root Tip (px)") +
      ylab("Velocity from Root Tip (px/frame)") +
      theme_bw())
    # Saving each graph as .tiff takes up more space than .pdf, so using .pdf for full RILSet
    graphName = paste('~/Desktop/RILPop_plots/', graphTitle, '_pointCloudFittedVel.pdf', sep = "")
    # Saves plot to location written above ^
    ggsave(graphName)
  }
}
####################################################################


####################################################################################
# 11-24-2020, Cases with very low mle value correlated w/ little/no mat zone:
# give flf parameters & gives REGR growth rate (slope at last 10 points of the fit)
## IF that slope isn't ~0, then you likely didn't get enough maturation zone
# Create code to report out the -log(mean(slope[last 10 position points - mat zone])) to the res structure summary table
## Added this to flf.R on 12.1.2020!
# wholePosVel = read.csv("/Users/ashleyhenry/Desktop/RILPop_full/RIL1_1/RIL1--RIL1_001_1.5--/rawData.csv", header = FALSE)
# wholePosVel = wholePosVel %>%
#   rename(
#     pos = V1,
#     vel = V2
#   )
# # plot(wholePosVel$pos, wholePosVel$vel)
# 
# resValue = 1 # only use if have a small res sample!
# # 1 - make flf fit line
# fittedVel = flf(wholePosVel$pos, 
#                 res[[resValue]]$summary_table[2]$x0,	
#                 res[[resValue]]$summary_table[3]$vf,	
#                 res[[resValue]]$summary_table[4]$k,	
#                 res[[resValue]]$summary_table[5]$n)
# fittedposVel = cbind(wholePosVel$pos, fittedVel) # makes matrix of pos & fitted vel values for g truth parameters
# fittedposVel = data.frame(fittedposVel) %>% # forces the matrix to be a dataframe
#   rename(pos = V1)
#   
# # RILSetAnalysisScript.Rmd version
# # 2 - take last 10 points on that line
# sortedpos = sort(fittedposVel$pos, decreasing = TRUE)
# srtpos = sortedpos[1:10]
# final10Points = fittedposVel %>%
#   filter(pos >= srtpos)
# 
# # Calculate slope for each of these points
# final10REGR = REGR(final10Points$pos, 
#      res[[resValue]]$summary_table[2]$x0,	
#      res[[resValue]]$summary_table[3]$vf,	
#      res[[resValue]]$summary_table[4]$k,	
#      res[[resValue]]$summary_table[5]$n,
#      1)
# # Take -log(mean(x))
# logmeanFinalPos = -log(mean(final10REGR))

# From res structure's Summary Table[matSlope]
# RIL1                - 13.84374
# RIL40 - no mat zone - 5.734695
# RIL83               - 13.14896
# RIL86               - 7.43973
# RIL99 - no mat zone - 6.216946
####################################################################################

####################################################################################
# 1 December 2020
# Defining the Maturation Zone: Finding points that are within the maturation zone
## This will help to see if roots with little/no mat zone should be removed from the data
resValue = 1 # Used RIL40 as example
pos = c(1:3000)
# Get REGR fits for example data
REGRtmp <- REGR(pos, 
                  res[[resValue]]$summary_table[2]$x0,	
                  res[[resValue]]$summary_table[3]$vf,	
                  res[[resValue]]$summary_table[4]$k,	
                  res[[resValue]]$summary_table[5]$n,
                  1)
# Get velocity fits for example data
fittedVel = flf(pos, 
                res[[resValue]]$summary_table[2]$x0,	
                res[[resValue]]$summary_table[3]$vf,	
                res[[resValue]]$summary_table[4]$k,	
                res[[resValue]]$summary_table[5]$n)

REGRfit = data.frame(cbind(pos, REGRtmp))
maxREGR = max(REGRtmp) # finds Vmax
per = 0.2 # percentage of area under the curve we want
maxVel = max(fittedVel) # finds vf

velocityFit = data.frame(cbind(pos, fittedVel))
plot(velocityFit)

ggplot(REGRfit, aes(x = pos)) +
  geom_point(aes(y = REGRtmp))

# find values that are outside of 20% of the REGR curve, and also greater than 50% of the max velocity values = points in the maturation zone
# Finds REGR points that are less than 20% of the max
## i.e. Draws line near bottom of REGR curve & grabs the points in meristematic & maturation zones
# AND THEN
# Finds Vel points that are greater than 50% of the max velocity
## i.e. Grabs the ~maturation~ part of the above selection
k = which((REGRtmp < maxREGR*per) & (fittedVel > maxVel*0.5)) 
# Boolian version of above (i.e. gives true/false version)
kbool = (REGRtmp < maxREGR*per) & (fittedVel > maxVel*0.5)

plot(kbool) # Should plot only the maturation zone, but doesn't...? Something's off here...


# 12-01-2020 at 5:00pm w/ Nathan:
# For every replicate: (AFTER THE FITTING, THIS IS SEPARATE)
## count number of datapoints fall within the maturation zone
## what % of points is that?

####################################################################################


# Saves res structure (technically a "large list") to the working directory
## Saves data in a binary file
save(res, file = "~/rildata/rildata_realfullDataset/2020_12_07_res_RILPop_full.RData")
save(res, file = "~/Desktop/pux1Imaging/2020_12_04_res_pux1Day3.RData")


```

# Note: The following code chunks are copied from combineResStructures.Rmd to have one Analysis Script instead of several scripts doing partial work

```{r Load-Res-Structures}

######################################################################
# Note: only use this if your whole RILset is alone in the directory #
#### Else it'll combine all .RData files in the chosen directory! ####
######################################################################

# Iteratively loads in all res structures from ~/rildata directory by:
## Loads RData file into new environment
## Then extracts res variable
loadRData <- function(fileName) {
  #loads an RData file, and returns it
  e1 = new.env()
  load(fileName, e1)
  get("res", e1)
}
# 
# Load in correct res structure
load("~/rildata/rildata_realfullDataset/2020_12_02_res_RILPop_full.RData")
load("~/Desktop/pux1Imaging/2020_12_04_res_pux1Day3.RData")


# Pulls filenames from directory
fils <- matrix(list.files("~/rildata/rildata_realfullDataset", pattern = "RData$", full.names = TRUE, recursive = TRUE))
fils <- matrix(list.files("~/Desktop/pux1Imaging", pattern = "RData$", full.names = TRUE, recursive = TRUE))

# # Loading them into RES structure
RES <- lapply(fils, loadRData)

# Shouldn't need thisas of 11.19.2020  
## Use if combined multiple res structures
# save(RES, file = "~/rildata/rildata_fullDataset/2020_10_21_allresStructures.RData")
```

```{r Combine-Summary-Tables-of-Res-Structure}
############## function & for loop written on 30 January 2020 w/ Julian's help #############
####################### Copied from ParameterInvestigation.Rmd script ######################
# Function to separate res structure and rename pathname to filename for column "fileName" #
pathname_to_filename = function(genotype) {
  # Get genotype name from pathname
  genoName = basename(dirname(dirname(toString(genotype$fileName[[1]]))))
  # Create empty matrix of one column and as many rows as there are of res structure
  outnames = matrix(1, nrow(genotype))
  # outnames = matrix(1, as.numeric(nrow(genotype)))
  # Loops through each row of res
  ## Extracts pathname from each row in the dataframe
  ## Extracts filename from each pathname
  ## outnames = extracted filenames
  for (i in 1:nrow(genotype)) {
    namePlay_i  = toString(genotype$fileName[[i]])
    outnames[i] = basename(dirname(namePlay_i))
    print(outnames[i])
  }
  # Replaces pathname column with outnames column
  ## Now the column labeled "fileName" has filename instead of pathname
  genotype[["fileName"]] <- outnames
  # Return genotype summary table and genotype name
  gtype_gname = list(genotype, genoName)
  return(gtype_gname)
}

extractParameters = function(res) {
  # Create empty dataframe to fill with each RIL's parameters
  RILParameterSummaryTable = data.frame(matrix(
                                            ncol = 7, 
                                            nrow = 0, 
                                            dimnames = list(NULL, c("fileName", "x0", "vf", "k", "n", "meanAbsDiff", "matSlope"))))

  # for loop to call "pathname_to_filename" function for each genotype in res
  ## Fills dataframe with all replicates of all RILs' parameter summary tables
  for (i in 1:length(res)) {
    gtype = res[[i]]$summary_table
    gList = pathname_to_filename(gtype)
    summaryTable = gList[[1]]
    eval(parse(text = paste0(sprintf("%s = gList[[1]]", gList[[2]]))))
    RILParameterSummaryTable = rbind(RILParameterSummaryTable, summaryTable)
  }

  return(RILParameterSummaryTable)
}

# Uses function above to make summary table for parameters of all RILs
RILParams = lapply(RES, extractParameters)
RILParam_concatenated = bind_rows(RILParams)
# RILParam_concatenated = bind_rows(fileName) 

# Save progress
save(RILParam_concatenated, file = "~/rildata/rildata_realfullDataset/2020_12_03_RILsSummaryParameters.csv")
save(RILParam_concatenated, file = "~/Desktop/pux1Imaging/2020_12_04_pux1Day3_SummaryParameters.csv")

```

```{r shorten-fileName-to-be-RILnumbers}
# This code chunk creates a new column called "RILs" and fills that column with the shortened fileName
## This allows the RILs to be grouped together and averaged, because now they have the same name to be grouped
## Note: Revised on 2020-05-27 to add leading zeros before RIL number

# Start with file you just created (^), need to load() then get() to have in environment
AllRILs_SummaryParameters = load("~/rildata/rildata_realfullDataset/2020_12_03_RILsSummaryParameters.csv")
AllRILs_SummaryParameters = load("~/Desktop/pux1Imaging/2020_12_04_pux1Day3_SummaryParameters.csv")
AllRILs_SummaryParameters = get(AllRILs_SummaryParameters)

# Use if only need one RIL (how do you get select.r?)
# RIL1_SummaryParameters = AllRILs_SummaryParameters %>%
#   select.r(RIL1)


# Makes a column of shortened RIL names by copying the fileName column
## Make copy of fileName column called RILs
AllRILs_SummaryParameters$RILs <- AllRILs_SummaryParameters$fileName

# Extracts the "RIL##" from fileName and fills in the "RILs" column
## This works for RILs, but need to correct for Cvi & Ler
AllRILs_SummaryParameters$RILs <- str_extract(AllRILs_SummaryParameters$RILs, "[A-Z]+[0-9]+")
AllRILs_SummaryParameters$RILs = str_extract(AllRILs_SummaryParameters$RILs, "[0-9]+")



AllRILs_SummaryParameters$genotype <- AllRILs_SummaryParameters$fileName
AllRILs_SummaryParameters$genotype = str_extract(AllRILs_SummaryParameters$genotype, "[^_]+")
AllRILs_SummaryParameters$genotype = str_split(AllRILs_SummaryParameters$genotype, '--', simplify = TRUE)[,1]


#############################################################################################
######################## Use this chunk if need to add leading zeros ########################
#############################################################################################
# # Extract only number from RIL##
# AllRILs_SummaryParameters$RILs <- str_extract(AllRILs_SummaryParameters$RILs, "[0-9]+")
# 
# # Make numbers numeric instead of characters to use sprintf()
# AllRILs_SummaryParameters$RILs <- as.numeric(AllRILs_SummaryParameters$RILs)
# # Use sprintf() to add "RIL_" leadingzeros to 3 digits "# of RIL"
# AllRILs_SummaryParameters$RILs <- sprintf("RIL%03d", AllRILs_SummaryParameters$RILs)
# ##### Note: This works for RIL numbers, but messes up with Cvi & Ler
# 
# # Replace RIL0NA with NA
# AllRILs_SummaryParameters$RILs <- str_replace(AllRILs_SummaryParameters$RILs, "RIL0NA", replacement = NA_character_)
#############################################################################################

#############################################################################################
##################### Use this accidentally kept Cvi and Ler in dataset #####################
#############################################################################################
# # Filter out NAs from the dataframe's RILs column (which are Cvi & Ler)
# ## Using string split(), and "--" as the separator
# ## Makes that output into a matrix (to index in next line)
# correctNAs = strsplit(AllRILs_SummaryParameters$fileName[is.na(AllRILs_SummaryParameters$RILs)], split = "--", fixed = TRUE)
# correctNAs = matrix(unlist(correctNAs), nrow = length(correctNAs), byrow = T)
# 
# # Takes column from above output that contains "Cvi" and "Ler" (this time it's 2nd column, hence correctNAs[,2])
# ## Replaces the NAs with "Cvi" and "Ler" strings
# AllRILs_SummaryParameters$RILs[is.na(AllRILs_SummaryParameters$RILs)] <- correctNAs[,2]


# Use if need to remove duplicate RILs
## Because the 1st code chunk loads one extra res file (Cvi, Ler & RILs1-10)
# AllRILs_SummaryParameters = AllRILs_SummaryParameters %>% 
#   distinct()


# Save progress in csv file
write.csv(AllRILs_SummaryParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_SummaryParameters.csv")
write.csv(AllRILs_SummaryParameters, "~/Desktop/pux1Imaging/2020_12_04_pux1Day3_SummaryParameters.csv")
```

```{r sample-size-balancing}
##### This code chunk: Need to find RILs w/ 8+ samples & randomly reduce that to 8 #####

# Load in data saved from previous code chunk ^
# Problem: also loads in rownames as 1st column, fix this?
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_SummaryParameters.csv")




# Variable for threshold of replicate numbers, may be used later so code is dynamic
# SAMPLETHRESH = 8

# Summary table subset that has column for RIL number and column for no. of replicates of that RIL no.
AllRILs_nParameters = AllRILs_SummaryParameters %>%
  group_by(RILs) %>%
  select(-X, -fileName) %>%
  tally() #%>%
  # filter(n >= SAMPLETHRESH)

# Save table with RIL & respective number of samples
write.csv(AllRILs_nParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_nParameters.csv")

#############################################################################################
################ Use this if need to level out sample numbers across dataset ################
#############################################################################################
# # Function to make data subset of RILs that have >5 replicates
# drawRILSamples = function(ril){
# 
#   # Takes in whole summary table of all RILs
#   rilSample = AllRILs_SummaryParameters %>% 
#     # Only filter out specified RIL replicates
#     ## "ril" in this case is a list of RILs that have >5 replicates (RILs2Sample below)
#     filter(RILs == ril)
#   # saves the RILs that have >8 replicates in data subset called randSample
#   randSample = sample_n(rilSample, SAMPLETHRESH)
#   # function output is data subset in randSample
#   return(randSample)
# }
# 
# # Creates list of RILs that are in the AllRILs_nParameters that have >8 replicates
# RILs2Sample = AllRILs_nParameters$RILs
# 
# # Uses drawRILSamples function to create data subset of randomly selected RILs from the list of RILs that contained >5 replicates
# subsetwCorrectedSampleSize = lapply(RILs2Sample, drawRILSamples) # right data (maybe?), wrong format
# # Fixed format of data subset with corrected replicate size
# subsetwCorrectedSampleSize = bind_rows(subsetwCorrectedSampleSize) # Ta daaaa
# 
# # Now make separate dataframe containing only RILs with <=5 replicates
# # Create list of RILs with okay relicate numbers
# subsetwFineSamples = AllRILs_SummaryParameters %>%
#   group_by(RILs) %>%
#   select(-X, -fileName) %>%
#   tally() %>%
#   filter(n < SAMPLETHRESH)
# 
# # Create data subset only containing RILs with correct number of replicates
# ## Will be binded with subset of data that just corrected replicate number
# subsetwFineSamples2 = AllRILs_SummaryParameters %>%
#   subset(RILs %in% subsetwFineSamples$RILs)
# 
# # The final dataframe containing corrected number of replicates for each RIL
# ## Please rename~~~~~~
# AllRILsCorrectedSampleSize = rbind(subsetwFineSamples2, subsetwCorrectedSampleSize) %>%
#   group_by(RILs) %>%
#   select(-X, -fileName)
# 
# # Save new dataset with corrected sample size (<= 5 samples) in csv file
# write.csv(AllRILsCorrectedSampleSize, "~/rildata/2020_08_23_AllRILs_CorrectedSampleSize_SummaryParameters.csv")

```

```{r log(Parameter)-stats-by-RIL}
# This code chunk is to average parameters per RIL to create a table for the input of the R/qtl2 package
## Uses output from previous code chunk "shorten-fileName-to-be-RILnumbers"
# Info needed from RILs:
log() # take log() of all parameters to make data more normal
mean() # average of that RIL's parameter -> won't use this b/c have non-normal data
median() # median of that RIL's parameter -> WILL use this b/c have non-normal data
sd() # st dev of that RIL's parameter
var() # variance of that RIL's parameter
tally() # No. of samples for each RIL

# Load in csv with corrected sample size data
# AllRILs_SummaryParameters = read.csv("~/rildata/2020_08_23_AllRILs_CorrectedSampleSize_SummaryParameters.csv")
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_SummaryParameters.csv")
AllRILs_SummaryParameters = read.csv("~/Desktop/pux1Imaging/2020_12_04_pux1Day5_SummaryParameters.csv")


# Take log of all parameters to produce more normal data
AllRILs_logParameters = AllRILs_SummaryParameters %>%
  # group_by(RILs) %>%
  # select(-X, -fileName, -mle) %>%
  # log(a,b) b = base for log, else R will calc ln()
  mutate(logK = log(AllRILs_SummaryParameters$k, 10)) %>%
  mutate(logN = log(AllRILs_SummaryParameters$n, 10)) #%>%
  # mutate(RIL = as.numeric(RILs))

# Use summarise_each and funs() to calculate stats for all parameters
## Group by RIL to group together & get stats for each RIL (not taking stat of whole pop)
## Removed X (rownames created from csv) and fileName column from dataframe
## Calc'd chosen stat via summarise_each(funs())
## PLEASE NOTE: mutate(RIL = as.numeric(RILs)) JUST NAMES THE RILS AS 1-162, WITHOUT RECOGNIZING WHICH RIL ITS COVERING!!!
### EXAMPLE: RIL10 = RIL2 B/C ITS THE 2ND RIL AFTER RIL1 IN THE "RILs" COLUMN!!! i.e. don't use this, unless you can fix it!
AllRILs_AveragedParameters = AllRILs_SummaryParameters %>%
# AllRILs_AveragedParameters = AllRILs_logParameters %>%

  # mutate(RIL = as.numeric(RILs)) %>%
  # group_by(RILs) %>% 
  group_by(genotype) %>% 
  select(-X, -fileName) %>%
  # select(-X, -fileName, -matSlope, -meanAbsDiff) %>% # Use if want to remove fitting metrics from dataset
  summarise_each(funs(mean(., na.rm = TRUE))) # Added na.rm so that averages didn't calc in the NAs for the mean

AllRILs_MedianParameters = AllRILs_logParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>% 
  select(-fileName, -X) %>%
  summarise_each(funs(median))

AllRILs_StDevParameters = AllRILs_logParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>%
  select(-X, -fileName) %>%
  summarise_each(funs(sd)) 

AllRILs_VarianceParameters = AllRILs_logParameters %>%
  # mutate(RIL = as.numeric(RILs)) %>%
  group_by(RILs) %>%
  select(-X, -fileName) %>%
  summarise_each(funs(var))

# AllRILs_nParameters = AllRILs_logParameters %>%
#   # mutate(RIL = as.numeric(RILs)) %>%
#   group_by(RILs) %>%
#   # select(-X, -fileName) %>%
#   tally()

# Save all files from above
write.csv(AllRILs_AveragedParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_AveragedParameters.csv")
write.csv(AllRILs_AveragedParameters, "~/Desktop/pux1Imaging/PRE-OUTLIERTEST_2020_12_04_pux1Day5_AveragedParameters.csv")

write.csv(AllRILs_MedianParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_MedianParameters.csv")
write.csv(AllRILs_StDevParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_StDevParameters.csv")
write.csv(AllRILs_VarianceParameters, "~/rildata/rildata_realfullDataset/2020_12_03_AllRILs_VarianceParameters.csv")
# write.csv(AllRILs_nParameters, "~/rildata/rildata_fullDataset/2020_10_08_AllRILs_nParameters.csv")
```

```{r brief-outlier-testing}
# install.packages("outliers")
library(outliers)
AllRILs_SummaryParameters = read.csv("~/rildata/rildata_fullDataset/2020_10_08_AllRILs_SummaryParameters.csv")

AllRILs_SummaryParameters = AllRILs_SummaryParameters %>%
  select(-X, -fileName) %>%
  group_by(RILs)

parametersMelted = melt(AllRILs_logParameters, id.var = "RILs")

# Boxplot to Visualize parameter distribution
ggplot(data = parametersMelted, aes(x = variable, y = value)) + 
  geom_boxplot(aes(fill = variable)) +
  ylab("") +
  xlab("Parameters") +
  ggtitle("Distribution of Parameters for Whole RIL Population") +
  theme_bw() +
  facet_wrap( ~ variable, scales = "free")

# Historgram of Parameters (FULL dataset)
ggplot(AllRILs_logParameters) +
  aes(x = x0) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = vf) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = logK) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()

ggplot(AllRILs_logParameters) +
  aes(x = logN) +
  geom_histogram(bins = 30L, fill = "#0c4c8a") +
  theme_minimal()


# Do distribution curves for each parameter in full dataset!
################# 2020_10_13 #################
## Overlying histogram & density plots
x0_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = x0)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=30,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(x0, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for x0 for Whole RIL Population") +
  theme_bw()

vf_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = vf)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=.3, # Change binwidth to match data (ex: x0 mean is ~300, need binwidth=30)
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(vf, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for vf for Whole RIL Population") +
  theme_bw()

logK_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = logK)) +
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=0.05,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(logK, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for logK for Whole RIL Population") +
  theme_bw()

logN_wholeRILPop = ggplot(AllRILs_logParameters, aes(x = logN)) + 
  geom_histogram(aes(y=..density..),      # Histogram with density instead of count on y-axis
                 binwidth=0.1,
                 colour="black", fill="white") +
  geom_density(alpha=.2, fill="#FF6666") +  # Overlay with transparent density plot
  geom_vline(aes(xintercept=mean(logN, na.rm=T)), # Ignore NA values for mean
                 color="red", linetype="dashed", size=1) +
  ggtitle("Density Plot for logN for Whole RIL Population") +
  theme_bw()




# Testing outliers using chisq test from the Outliers Package in R
## Should I divide these up by RILs and then by phenotype?
chisq.out.test(AllRILs_SummaryParameters$x0, variance=var(AllRILs_SummaryParameters$x0), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$x0, variance=var(AllRILs_SummaryParameters$x0), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$vf, variance=var(AllRILs_SummaryParameters$vf), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$vf, variance=var(AllRILs_SummaryParameters$vf), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$k, variance=var(AllRILs_SummaryParameters$k), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$k, variance=var(AllRILs_SummaryParameters$k), opposite = TRUE) # TRUE=highest value

chisq.out.test(AllRILs_SummaryParameters$n, variance=var(AllRILs_SummaryParameters$n), opposite = FALSE) # FALSE=lowest value
chisq.out.test(AllRILs_SummaryParameters$n, variance=var(AllRILs_SummaryParameters$n), opposite = TRUE) # TRUE=highest value

```

```{r fittingVelCurves}
### Creates numeric vector for means of the parameters ###
### Makes range of y from 0.0 to 3.5 px/hr ###
### pos values range from 0-2000 px from QC, increasing by 1 px at a time ###
ku         <- vector('numeric')
range_of_y <- range(0, 3.5)
pos        <- seq(0, 2000, 1)

```

```{r EvaluateVelandREGRFits}
# Note: This code chunk is copied from AnalyzeKinematic[...].Rmd
# Loops through all genotypes/conditions evaluating the equation at a 
## value, Pos (fixed position values (0-2000, increments of 1)), to 
## calculate velocity and REGR values using the maximum likelihood 
## estimate parameters for each replicate
# WARNING: Fits ALL replicates, not the average. To fit the avg vel, 
## look to the next code chunk
# Please Note: The final product has the correct units (hallelujah!)

for (i in 1:length(res)) {
  resultVel <- evaluateVelFits(res[[i]], pos)
  matrixEnd = ncol(resultVel) - 1
  for (j in 2:matrixEnd) {
    resultVel[,j] <- as.numeric(resultVel[,j]) * 0.08202 } # conversion from px/frame to mm/hr for all velocity value columns
  resultVel[,1] = as.numeric(resultVel[,1]) / 1463 # conversion from px to mm for the one position value column
  write.csv(resultVel, paste('/Users/ashleyhenry/Desktop/PosEvaluatedVel', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultVel[,1], resultVel[,2])
  
  ######################################
  
  resultREGR <- evaluateREGRFits(res[[i]], pos, 120*100)
  matrixEnd = ncol(resultREGR) - 1
  
  # for (k in 2:matrixEnd) {
    # resultREGR[,j] <- as.numeric(resultREGR[,j]) * 120} # DOESN'T WORK: conversion from px/frame*frame to px/frame*hr (or %/hr) for all velocity value columns
  
  resultREGR[,1] = as.numeric(resultREGR[,1]) / 1463 # WORKS: conversion from px to mm for the one position value column
  write.csv(resultREGR, paste('/Users/ashleyhenry/Desktop/PosEvaluatedREGR', as.numeric(i), '.csv', sep = ""), row.names = F)
  plot(resultREGR[,1], resultREGR[,2])
}
```



